---
title: "validvac_seasonalFixed_Appendices"
author: "Beth Savagar"
date: "2023-12-11"
output: html_document
---

# Script for immunity analysis of flock profiles with seasonal reproduction:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library}
# libraries not accounted for in setup script
library(GGally)
plotsave <- F
custom_theme <- theme_bw() + theme(text = element_text(family = "Times New Roman", size = 9))
theme_set(custom_theme)
# custom_palette <- c("#004D40", "#00695C", "#00796B", "#00897B", "#009688", "#4A148C", "#6A1B9A", "#7B1FA2", "#8E24AA", "#9C27B0")

```

```{r modSetup1}
############
## SETUP ##
############
local <- T
# local filepath: 
if(local){
  filepath <- ""
}else{
  # cluster filepath
  filepath <- "/storage/users/bsavagar/"
}

## Libraries
source(paste0(filepath,"scripts/setup.R")) 

## Functions:
source(paste0(filepath, "functions/Appliedfunc_seasonalfixed.R")) # wrapper function
source(paste0(filepath, "functions/demos_summary.R")) # summary stats for output
source(paste0(filepath, "functions/dynmod-vac_seasonalfixed.R")) # flock dynamics model function
source(paste0(filepath, "functions/output.R")) # what to include in output df
source(paste0(filepath, "functions/GSA_outputs.R")) # summary stats accounting for vac

```


```{r selectData}
# 9/11/23: Run model with LHS of oc parameter space. Analyse results against original valid population conditions and against oc population growth reports. 

applied_example <- T

## Load parameters
datafile <- "-OC_validPars-seasonal"
fix_age_data_full <- read_csv(paste0("data/Applied_parameters/state_vars",datafile,".csv"),col_names=T)
var_demo_data_full <- read_csv(paste0("output/Applied/applied_outValidPars_OC_2023-12-11.csv"))
# load mean annual birth rate (calc from validVac non-seasonal.Rmd)
nBirths_df <- read_csv("output/Applied/stableAgeSex/Applied_nBirths_OC.csv")
imm_decay_corrected <- read_csv("data/imm_decay_bodjo_v2.csv") 

## Datasets
datasets <- fix_age_data_full %>% select(-parameter) %>% colnames()
#combine nBirths with other demogrpahics
var_demo_data_full <- var_demo_data_full %>%
  mutate(nBirths_yr = nBirths_df$mean)

```

```{r modSetup}

######################
## MODEL SETUP ##
######################

## Simulation:
TimeStop_dynamics <- 20*52 # 2 years only interested in rates for 1 y
TimeStop_transmission <- 24 # 1 day, hourly timestep for transmission component
min_pop <- 1 # set minimum size of population, if pop drops below then set to 0


##################
## RUN MODEL ##
##################

turnover <- F; 
dynamics <- T; 
transmission <- F; 
clean_environment <- T
seasonal <- T

# timepoints for population growth
t2 <- TimeStop_dynamics/2 # 5 year pop growth
t1 <- TimeStop_dynamics


##################################
## BIRTH PEAKS  ##
##################################

# id which week of the year each month starts on:
wkmnthids <- data.frame(
  mnth = 1:12,
  mnthwk = seq(1,53, by = 4.345) %>% round()
)

peakmnth <- 1  # Month of peak
peakstart <- wkmnthids %>% filter(mnth == peakmnth) %>% pull()
pkwk1 <- seq(from=peakstart, by=1, length.out=4)
birthpeak_w <- c()
time_yrs <- TimeStop_dynamics/52
for(i in 1:time_yrs-1){
  seqjump <- i*52
  pkwki <- pkwk1+seqjump
  birthpeak_w <- c(birthpeak_w,pkwki)
}

##################################
## LHS SETUP  ##
##################################

lhs <- F
lhs_n <- 0 # number of sets (parameter combinations)
pairs_plot <- F
SA <- F

```

Vaccination simulations:
- 4 rounds: year 1-2: >4m, year 3-4: 4m-12m
- coverages: 70,80,90,100
- schedules: 3m,6m,9m before birth peak
Appendices:
- Optimal vaccination schedule: 
    - y1 = ~6m before birth peak (high proportion of eligible animals & mat antibodies passed on to offspring)
    - y2 onwards = 3-4m after birth peak when offspring have lost maternal immunity
    --> V1 (-6m), V2 = +10m after V1, V3 = +1y after V2, 


```{r vaccinationSchedule}

#######################
## Vaccination Setup ##
#######################
# see applied_vaccination
pVs <-c(0.7,0.8,0.9,1)
pV <- 1

## GSCE Vaccination: 
V_rounds <- 3 # number of campaigns (GSCE recommended)
V_breaks <- 52 # uneven

# 6 months before birth peak:
V1 = round(t2+(6*4.345),0)
V2 = round(V1 + 11*4.345) # 10m after first vaccination (when offspring become susceptible)
V3 = round(V2 + 52) # 12m after second round (when offspring become susceptible)
# V4 = V3 + 10*4.345

V_age_min <- round(4 *4.345,0) # 4 months (4.345 weeks per month)
# *** Update to 16m so no animal is missed ***
V_age_max <- round(12*4.345,0) # 12 months (4.345 weeks per month) for partial campaigns

Vprog <- data.frame(
  Vround = 1:V_rounds,
  Vtype = c("full","partial","partial"),
  Vweek = c(V1,V2,V3),
  Vmin = V_age_min,
  Vmax = c(NA, V_age_max, V_age_max),
  pV = rep(pV, V_rounds)
)

Vstart <- Vprog %>% filter(Vround==1) %>% pull(Vweek)

```


# Simulate full immunity dynamics following vaccination for all OC profiles with non-seasonal reproduction

```{r DynLoop}

###################
## MODEL OUTPUT ##
###################
seasonal <- T
## Model Output
output <- "dynamics" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

# validOut = list to store outputs
GSAoutput <- c(); 
ocOut.seasonal <- list()

#####################
## DATA SELECTION ##
#####################

dataset <- datasets

if (dataset == "lesnoff.ft") {
  rates <- "wkly"
} else{
  rates <- "yrly"
}

fixdata <- dataset # set dataset for state_vars
vardata <- dataset
  
# filter to profiles with non-seasonal reproduction
var_demo_data_profs <- var_demo_data_full %>%
  filter(prof %in% c("oc.goat.aridP",
                     "oc.goat.semiaridP",
                     "oc.shp.aridP",
                     "oc.shp.semiaridP"))

profOrder <- var_demo_data_profs %>% select(prof) %>% pull()
var_input_backup <- var_demo_data_profs %>% select(-prof)

```

```{r runMod}

#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")

A.seasonal <- c()
Adyn_i.clean <- c() # dataframe for expanded immunity dynamics


for(v in 1:length(pVs)){
  
  Vprog$pV <- rep(pVs[v], V_rounds)
    
  Vstart <- Vprog %>% filter(Vround==1) %>% pull(Vweek)
  
  A.seasonal <- foreach (i = 1:nrow(var_input_backup),
                           .packages = c("dplyr", "tibble")) %dopar% {
                             print(i)
                             
                             var_input_full <- unlist(var_input_backup[i,])
                             
                             App_func(
                               imm_decay_corrected,
                               var_input_full,
                               fix_age_data_full,
                               f_list,
                               # initial state of female population
                               m_list,
                               # initial state of male population
                               TimeStop_dynamics,
                               # 1 year, weekly timestep for demographic component
                               TimeStop_transmission,
                               # 1 day, hourly timestep for transission component
                               output,
                               # model output: tracker or summary stats
                               summary_df,
                               #
                               clean_environment,
                               Vstart,
                               Vprog,
                               fixdata,
                               vardata,
                               birthpeak_w,
                               seasonal
                             )
                           }
  
  Adyn_i <- lapply(A.seasonal , select, prop_immune) %>%
  bind_cols() %>%
  t() %>%
  as.data.frame()
  
  colnames(Adyn_i) <- 1:ncol(Adyn_i)
  rownames(Adyn_i) <- 1:nrow(Adyn_i)
  
  Adyn_i.clean <- Adyn_i.clean %>% 
    bind_rows(
      Adyn_i %>%
        select((t2):ncol(Adyn_i)) %>%
        mutate(prof = profOrder,
               pV = pVs[v])
    )
  }

stopCluster(cl)

```

```{r DynamicsAnalysis}

AimmDynamics.long <- Adyn_i.clean %>%
  gather(key = "weeks", value = "prop_immune", -c(prof, pV)) %>%
  mutate(weeks = as.numeric(weeks))

# Calculate mean and confidence interval
Asummary_data <- AimmDynamics.long %>%
  group_by(pV,prof,weeks) %>%
  summarise(
    mean_value = mean(prop_immune),
    lower_ci = quantile(prop_immune, 0.025),
    upper_ci = quantile(prop_immune, 0.975)
  )

plotA_immVar <- ggplot(Asummary_data, aes(x = weeks, y = mean_value, group = factor(pV))) +
  #geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci, fill = factor(pV)), alpha = 0.5) +
  geom_line(aes(col = factor(pV))) +
  geom_hline(yintercept = 0.7, linetype = "dashed")+
  facet_wrap(~prof)+ # facet_grid(pV~prof)+
  guides(fill = "none")+
  labs(x="Time (weeks)", y = "Proportion Immune", col = "pV")+
  coord_cartesian(xlim = c(500,750))

plotA_immVar
# 
# filename_immVar <- "OC_seasonalDyn.png"
# ggsave(paste0("plots/applied/",filename_immVar), plot = plot_immVar, width = 20, height = 10, units = "cm")

```



```{r vaccinationSchedule}

#######################
## Vaccination Setup ##
#######################
# see applied_vaccination
pVs <-c(0.7,0.8,0.9,1)
pV <- 1

## GSCE Vaccination: 
V_rounds <- 3 # number of campaigns (GSCE recommended)
V_breaks <- 52 # uneven

# 6 months before birth peak:
V1 = round(t2+(6*4.345),0)
V2 = round(V1 + 9*4.345) # 10m after first vaccination (when offspring become susceptible)
V3 = round(V2 + 52) # 12m after second round (when offspring become susceptible)
# V4 = V3 + 10*4.345

V_age_min <- round(2*4.345,0) # 4 months (4.345 weeks per month)
# *** Update to 16m so no animal is missed ***
V_age_max <- round(12*4.345,0) # 12 months (4.345 weeks per month) for partial campaigns

Vprog <- data.frame(
  Vround = 1:V_rounds,
  Vtype = c("full","partial","partial"),
  Vweek = c(V1,V2,V3),
  Vmin = V_age_min,
  Vmax = c(NA, V_age_max, V_age_max),
  pV = rep(pV, V_rounds)
)

Vstart <- Vprog %>% filter(Vround==1) %>% pull(Vweek)

```


# Simulate full immunity dynamics following vaccination for all OC profiles with non-seasonal reproduction

```{r DynLoop}

###################
## MODEL OUTPUT ##
###################
seasonal <- T
## Model Output
output <- "dynamics" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

# validOut = list to store outputs
GSAoutput <- c(); 
ocOut.seasonal <- list()

#####################
## DATA SELECTION ##
#####################

dataset <- datasets

if (dataset == "lesnoff.ft") {
  rates <- "wkly"
} else{
  rates <- "yrly"
}

fixdata <- dataset # set dataset for state_vars
vardata <- dataset
  
# filter to profiles with non-seasonal reproduction
var_demo_data_profs <- var_demo_data_full %>%
  filter(prof %in% c("oc.goat.aridP",
                     "oc.goat.semiaridP",
                     "oc.shp.aridP",
                     "oc.shp.semiaridP"))

profOrder <- var_demo_data_profs %>% select(prof) %>% pull()
var_input_backup <- var_demo_data_profs %>% select(-prof)

```

```{r runMod}

#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")

A.seasonal <- c()
Adyn_i.clean <- c() # dataframe for expanded immunity dynamics


for(v in 1:length(pVs)){
  
  Vprog$pV <- rep(pVs[v], V_rounds)
    
  Vstart <- Vprog %>% filter(Vround==1) %>% pull(Vweek)
  
  A.seasonal <- foreach (i = 1:nrow(var_input_backup),
                           .packages = c("dplyr", "tibble")) %dopar% {
                             print(i)
                             
                             var_input_full <- unlist(var_input_backup[i,])
                             
                             App_func(
                               imm_decay_corrected,
                               var_input_full,
                               fix_age_data_full,
                               f_list,
                               # initial state of female population
                               m_list,
                               # initial state of male population
                               TimeStop_dynamics,
                               # 1 year, weekly timestep for demographic component
                               TimeStop_transmission,
                               # 1 day, hourly timestep for transission component
                               output,
                               # model output: tracker or summary stats
                               summary_df,
                               #
                               clean_environment,
                               Vstart,
                               Vprog,
                               fixdata,
                               vardata,
                               birthpeak_w,
                               seasonal
                             )
                           }
  
  Adyn_i <- lapply(A.seasonal , select, prop_immune) %>%
  bind_cols() %>%
  t() %>%
  as.data.frame()
  
  colnames(Adyn_i) <- 1:ncol(Adyn_i)
  rownames(Adyn_i) <- 1:nrow(Adyn_i)
  
  Adyn_i.clean <- Adyn_i.clean %>% 
    bind_rows(
      Adyn_i %>%
        select((t2):ncol(Adyn_i)) %>%
        mutate(prof = profOrder,
               pV = pVs[v])
    )
  }

stopCluster(cl)

```

```{r DynamicsAnalysis}

AimmDynamics.long <- Adyn_i.clean %>%
  gather(key = "weeks", value = "prop_immune", -c(prof, pV)) %>%
  mutate(weeks = as.numeric(weeks))

# Calculate mean and confidence interval
Asummary_data <- AimmDynamics.long %>%
  group_by(pV,prof,weeks) %>%
  summarise(
    mean_value = mean(prop_immune),
    lower_ci = quantile(prop_immune, 0.025),
    upper_ci = quantile(prop_immune, 0.975)
  )

plotA_immVar <- ggplot(Asummary_data, aes(x = weeks, y = mean_value, group = factor(pV))) +
  #geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci, fill = factor(pV)), alpha = 0.5) +
  geom_line(aes(col = factor(pV))) +
  geom_hline(yintercept = 0.7, linetype = "dashed")+
  facet_wrap(~prof)+ # facet_grid(pV~prof)+
  guides(fill = "none")+
  labs(x="Time (weeks)", y = "Proportion Immune", col = "pV")+
  coord_cartesian(xlim = c(500,750))

plotA_immVar

# filename_immVar <- "OC_seasonalDyn.png"
# ggsave(paste0("plots/applied/",filename_immVar), plot = plot_immVar, width = 20, height = 10, units = "cm")

```
