---
title: "validvac_nonseasonalFixed"
author: "Beth Savagar"
date: "2023-12-11"
output: html_document
---

# Script for immunity analysis of flock profiles with nonseasonal reproduction:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library}
# libraries not accounted for in setup script
library(GGally)
plotsave <- F
custom_theme <- theme_bw() + theme(text = element_text(family = "Times New Roman", size = 9))
theme_set(custom_theme)
# custom_palette <- c("#004D40", "#00695C", "#00796B", "#00897B", "#009688", "#4A148C", "#6A1B9A", "#7B1FA2", "#8E24AA", "#9C27B0")

```

```{r modSetup1}
############
## SETUP ##
############
local <- T
# local filepath: 
if(local){
  filepath <- ""
}else{
  # cluster filepath
  filepath <- "/storage/users/bsavagar/"
}

## Libraries
source(paste0(filepath,"scripts/setup.R")) 

## Functions:
source(paste0(filepath, "functions/Appliedfunc_seasonalfixed.R")) # wrapper function
source(paste0(filepath, "functions/demos_summary.R")) # summary stats for output
source(paste0(filepath, "functions/dynmod-vac_seasonalfixed.R")) # flock dynamics model function
source(paste0(filepath, "functions/output.R")) # what to include in output df
source(paste0(filepath, "functions/GSA_outputs.R")) # summary stats accounting for vac

```


```{r selectData}
# 9/11/23: Run model with LHS of oc parameter space. Analyse results against original valid population conditions and against oc population growth reports. 

applied_example <- T

## Load parameters
datafile <- "-OC_validPars-seasonal"
fix_age_data_full <- read_csv(paste0("data/Applied_parameters/state_vars",datafile,".csv"),col_names=T)
var_demo_data_full <- read_csv(paste0("output/Applied/applied_outValidPars_OC_2023-12-11.csv"))
# load mean annual birth rate (calc from validVac non-seasonal.Rmd)
nBirths_df <- read_csv("output/Applied/stableAgeSex/Applied_nBirths_OC.csv")
imm_decay_corrected <- read_csv("data/imm_decay_bodjo_v2.csv") 

## Datasets
datasets <- fix_age_data_full %>% select(-parameter) %>% colnames()
#combine nBirths with other demogrpahics
var_demo_data_full <- var_demo_data_full %>%
  mutate(nBirths_yr = nBirths_df$mean)

```

```{r modSetup}

######################
## MODEL SETUP ##
######################

## Simulation:
TimeStop_dynamics <- 20*52 # 2 years only interested in rates for 1 y
TimeStop_transmission <- 24 # 1 day, hourly timestep for transmission component
min_pop <- 1 # set minimum size of population, if pop drops below then set to 0


##################
## RUN MODEL ##
##################

turnover <- F; 
dynamics <- T; 
transmission <- F; 
clean_environment <- T
seasonal <- T

# timepoints for population growth
t2 <- TimeStop_dynamics/2 # 5 year pop growth
t1 <- TimeStop_dynamics


##################################
## BIRTH PEAKS  ##
##################################

# id which week of the year each month starts on:
wkmnthids <- data.frame(
  mnth = 1:12,
  mnthwk = seq(1,53, by = 4.345) %>% round()
)

peakmnth <- 1  # Month of peak
peakstart <- wkmnthids %>% filter(mnth == peakmnth) %>% pull()
pkwk1 <- seq(from=peakstart, by=1, length.out=4)
birthpeak_w <- c()
time_yrs <- TimeStop_dynamics/52
for(i in 1:time_yrs-1){
  seqjump <- i*52
  pkwki <- pkwk1+seqjump
  birthpeak_w <- c(birthpeak_w,pkwki)
}

##################################
## LHS SETUP  ##
##################################

lhs <- F
lhs_n <- 0 # number of sets (parameter combinations)
pairs_plot <- F
SA <- F

```

Vaccination simulations:
- 4 rounds: year 1-2: >4m, year 3-4: 4m-12m
- coverages: 70,80,90,100
- schedules: annual, 6-monthly

Appendices:
- 3 rounds: year 1-2: >4m, year 3: 4m-12m
- lower minimum age of vaccination: 2y
- raise upper limit for vaccination in year 3-4: 16m
- schedules (annual, 6-monthly)

```{r vaccinationSchedule}

#######################
## Vaccination Setup ##
#######################
# see applied_vaccination
pVs <-c(0.7,0.8,0.9,1)
pV <- 1
# source("scripts/applied/applied_vaccination.R")


## GSCE Vaccination: 

# vaccination starts at halfway point of simulation
V1 <- 0.5*TimeStop_dynamics # first vaccination campaign
V_rounds <- 4 # number of campaigns (GSCE recommended)
V_breaks <- 52 # timesteps between campaigns: 1 year gaps with 1 week timestep

V_starts <- vector(length=V_rounds)
for(v in 1:V_rounds){
  V_starts[v] <- V1+(v-1)*V_breaks
}

V_age_min <- round(4 *4.345,0) # 4 months (4.345 weeks per month)
V_age_max <- round(12*4.345,0) # 12 months (4.345 weeks per month) for partial campaigns

Vprog <- data.frame(
  Vround = 1:V_rounds,
  Vtype = c("full","full","partial", "partial"),
  Vweek = V_starts,
  Vmin = V_age_min,
  Vmax = c(NA, NA, V_age_max, V_age_max),
  pV = rep(pV, V_rounds)
)

Vstart <- Vprog %>% filter(Vround==1) %>% pull(Vweek)


```


# Simulate full immunity dynamics following vaccination for all OC profiles with non-seasonal reproduction

```{r DynLoop}

###################
## MODEL OUTPUT ##
###################
seasonal <- F
## Model Output
output <- "dynamics" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

# validOut = list to store outputs
GSAoutput <- c(); 
ocOut.nonseasonal <- list()

#####################
## DATA SELECTION ##
#####################

dataset <- datasets

if (dataset == "lesnoff.ft") {
  rates <- "wkly"
} else{
  rates <- "yrly"
}

fixdata <- dataset # set dataset for state_vars
vardata <- dataset
  
# filter to profiles with non-seasonal reproduction
var_demo_data_profs <- var_demo_data_full %>%
  filter(!prof %in% c("oc.goat.aridP",
                     "oc.goat.semiaridP",
                     "oc.shp.aridP",
                     "oc.shp.semiaridP"))

profOrder <- var_demo_data_profs %>% select(prof) %>% pull()
var_input_backup <- var_demo_data_profs %>% select(-prof)

```

```{r runMod}

#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")

ocOut.nonseasonal.list <- c()

for(v in 1:length(pVs)){
  Vprog$pV <- pVs[v]
  
  ocOut.nonseasonal <- foreach (i = 1:nrow(var_input_backup),
                           .packages = c("dplyr", "tibble")) %dopar% {
                             print(i)
                             
                             var_input_full <- unlist(var_input_backup[i,])
                             
                             App_func(
                               imm_decay_corrected,
                               var_input_full,
                               fix_age_data_full,
                               f_list,
                               # initial state of female population
                               m_list,
                               # initial state of male population
                               TimeStop_dynamics,
                               # 1 year, weekly timestep for demographic component
                               TimeStop_transmission,
                               # 1 day, hourly timestep for transission component
                               output,
                               # model output: tracker or summary stats
                               summary_df,
                               #
                               clean_environment,
                               Vstart,
                               Vprog,
                               fixdata,
                               vardata,
                               birthpeak_w,
                               seasonal
                             )
                           }
  
  
  
  ocOut.nonseasonal.list[[v]] <- ocOut.nonseasonal 
}

stopCluster(cl)

```

```{r DynamicsAnalysis}

immDynamics.clean <- c() # dataframe for expanded immunity dynamics

for(l in 1:length(pVs)){
  dynamics_i <- ocOut.nonseasonal.list[[l]]
  
  immDynamics <- lapply(dynamics_i, select, prop_immune) %>%
  bind_cols() %>%
  t() %>%
  as.data.frame()
  
  colnames(immDynamics) <- 1:ncol(immDynamics)
  rownames(immDynamics) <- 1:nrow(immDynamics)
  
  immDynamics.clean <- immDynamics.clean %>% 
    bind_rows(
      immDynamics %>%
        select((t2):ncol(immDynamics)) %>%
        mutate(prof = profOrder,
               pV = pVs[l])
    )
    
}

# library(purrr)
# 
# immDynamics.clean <- map_dfr(ocOut.nonseasonal.list, function(dynamics_i) {
#   immDynamics <- lapply(dynamics_i, select, prop_immune) %>%
#     bind_cols() %>%
#     t() %>%
#     as.data.frame()
# 
#   colnames(immDynamics) <- 1:ncol(immDynamics)
#   rownames(immDynamics) <- 1:nrow(immDynamics)
# 
#   immDynamics %>%
#     select((t2):ncol(immDynamics)) %>%
#     mutate(prof = profOrder, pV = pVs) %>%
#     bind_rows()
# })


immDynamics.long <- immDynamics.clean %>%
  gather(key = "weeks", value = "prop_immune", -c(prof, pV)) %>%
  mutate(weeks = as.numeric(weeks))

# Calculate mean and confidence interval
summary_data <- immDynamics.long %>%
  group_by(pV,prof,weeks) %>%
  summarise(
    mean_value = mean(prop_immune),
    lower_ci = quantile(prop_immune, 0.025),
    upper_ci = quantile(prop_immune, 0.975)
  )

plot_immVar <- ggplot(summary_data, aes(x = weeks, y = mean_value)) +
  geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci, fill = factor(pV)), alpha = 0.5) +
  geom_line(aes(col = factor(pV))) +
  geom_hline(yintercept = 0.7, linetype = "dashed")+
  facet_wrap(~prof)+ # facet_grid(pV~prof)+
  guides(fill = "none")+
  labs(x="Time (weeks)", y = "Proportion Immune", col = "pV")+
  coord_cartesian(xlim = c(500,750))

plot_immVar

filename_immVar <- "OC_nonseasonalDyn_V12m.png"
ggsave(paste0("plots/applied/",filename_immVar), plot = plot_immVar, width = 20, height = 10, units = "cm")

```


```{r runMod2}

seasonal <- F
## Model Output
output <- "summary_all" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

# validOut = list to store outputs
GSAoutput <- c(); 
ocOut.nonseasonalSumm <- list()

#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")

ocOut.nonseasonalSumm.list <- c()


for(v in 1:length(pVs)){
  Vprog$pV <- pVs[v]
  
  summ_i <- foreach (i = 1:nrow(var_input_backup),
                           .packages = c("dplyr", "tibble"),
                           .combine = "rbind") %dopar% {
                             print(i)
                             
                             var_input_full <- unlist(var_input_backup[i,])
                             
                             App_func(
                               imm_decay_corrected,
                               var_input_full,
                               fix_age_data_full,
                               f_list,
                               # initial state of female population
                               m_list,
                               # initial state of male population
                               TimeStop_dynamics,
                               # 1 year, weekly timestep for demographic component
                               TimeStop_transmission,
                               # 1 day, hourly timestep for transission component
                               output,
                               # model output: tracker or summary stats
                               summary_df,
                               #
                               clean_environment,
                               Vstart,
                               Vprog,
                               fixdata,
                               vardata,
                               birthpeak_w,
                               seasonal
                             )
                           }

ocOut.nonseasonalSumm <- bind_rows(ocOut.nonseasonalSumm,
                                summ_i %>% mutate(pV = pVs[v],
                                                  prof = profOrder))
}

stopCluster(cl)

```

# Summary Stats


## add weeks over 70% to the output (in 4 year period)

from Vstart to Vstart+4y, tally 1 if over 70%, 0 if not, count the 1s


```{r ocOut.seasonalSumm}

ocOut.summdf <- ocOut.nonseasonalSumm %>%
  mutate(prof_group = ifelse(grepl("*shp*", prof), "shp", "goat"),
    prof = factor(
      prof,
      levels = c("oc.goat.aridP","oc.shp.aridP","oc.goat.semiaridP","oc.shp.semiaridP","oc.goat.semiaridM","oc.shp.semiaridM","oc.goat.subhumidM","oc.shp.subhumidM","oc.goat.humidM", "oc.shp.humidM")))

validImm <- ocOut.summdf %>%
  select(tenyr_growth, starts_with("imm"), pV, prof, prof_group) %>%
  gather(key = "stat", value = "value", -c(prof,prof_group, pV)) %>%
  mutate(stat = factor(stat, levels = c("imm_V0", "imm_6m", "imm_12m", "imm70_w", "imm70_wAll", "tenyr_growth" )))

plot_imm <- ggplot(validImm %>% filter(stat %in% c("imm_V0", "imm_6m", "imm_12m")), 
       aes(x = prof, y = value, group = prof))+ 
    geom_boxplot(alpha = 0.5, aes(fill = prof)) +
    geom_hline(yintercept = 0.7, linetype = "dashed")+
    facet_grid(pV~stat)+
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
          legend.position = "none")+
  scale_fill_brewer(palette = "Dark2")

plot_imm

plot_imm70 <- ggplot(validImm %>% filter(stat %in% c("imm70_w")), 
            aes(x = value, y = prof))+ #, col = peakmnth
  geom_boxplot(alpha = 0.5, fill = "grey") +
  geom_vline(xintercept = 26, linetype = "dashed")+
 facet_grid(pV~stat, scales = "free")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "none")
plot_imm70

plot_imm70All <- ggplot(validImm %>% filter(stat %in% c("imm70_wAll")), 
            aes(x = value, y = prof))+ #, col = peakmnth
  geom_boxplot(alpha = 0.5, fill = "grey")+
 facet_grid(pV~stat, scales = "free")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "none")
plot_imm70All

plot_tenyr <- ggplot(validImm %>% filter(stat %in% c("tenyr_growth")), 
            aes(x = prof, y = value))+ # , col = peakmnth
  geom_boxplot(alpha = 0.5, fill = "grey") +
  facet_grid(pV~stat, scales = "free")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "none")
plot_tenyr


filename_imm <- "OC_nonseasonalImm_V12m.png"
filename_imm70 <- "OC_nonseasonalImm70_V12m.png"
filename_imm70All <- "OC_nonseasonalImm70All_V12m.png"

if(plotsave){
  ggsave(paste0("plots/applied/",filename_imm), plot = plot_imm, width = 10, height = 20, units = "cm")
  ggsave(paste0("plots/applied/",filename_imm70), plot = plot_imm70, width = 10, height = 10, units = "cm")
  ggsave(paste0("plots/applied/",filename_imm70All), plot = plot_imm70All, width = 10, height = 10, units = "cm")
  
  }

```


#############################################
## 6 Month Vaccination
#############################################


```{r vaccinationSchedule}

#######################
## Vaccination Setup ##
#######################
# see applied_vaccination
pVs <- c(0.7,0.8,0.9,1)
pV <- 1
# source("scripts/applied/applied_vaccination.R")


## GSCE Vaccination: 

# vaccination starts at halfway point of simulation
V1 <- 0.5*TimeStop_dynamics # first vaccination campaign
V_rounds <- 8 # number of campaigns (GSCE recommended)

## Update V_breaks to 26 (half a year)
V_breaks <- 26 # timesteps between campaigns: 1 year gaps with 1 week timestep

V_starts <- vector(length=V_rounds)
for(v in 1:V_rounds){
  V_starts[v] <- V1+(v-1)*V_breaks
}

V_age_min <- round(4 *4.345,0) # 4 months (4.345 weeks per month)
V_age_max <- round(12*4.345,0) # 12 months (4.345 weeks per month) for partial campaigns

Vprog6 <- data.frame(
  Vround = 1:V_rounds,
  Vtype = c(rep("full",4),rep("partial", 4)),
  Vweek = V_starts,
  Vmin = V_age_min,
  Vmax = c(rep(NA, 4), rep(V_age_max, 4)),
  pV = rep(pV, V_rounds)
)

Vstart <- Vprog6 %>% filter(Vround==1) %>% pull(Vweek)


```


```{r DynLoop}

###################
## MODEL OUTPUT ##
###################
seasonal <- F
## Model Output
output <- "dynamics" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

# validOut = list to store outputs
GSAoutput <- c(); 
ocOut.nonseasonal6 <- list()

#####################
## DATA SELECTION ##
#####################

dataset <- datasets

if (dataset == "lesnoff.ft") {
  rates <- "wkly"
} else{
  rates <- "yrly"
}

fixdata <- dataset # set dataset for state_vars
vardata <- dataset
  
# filter to profiles with non-seasonal reproduction
var_demo_data_profs <- var_demo_data_full %>%
  filter(!prof %in% c("oc.goat.aridP",
                     "oc.goat.semiaridP",
                     "oc.shp.aridP",
                     "oc.shp.semiaridP"))

profOrder <- var_demo_data_profs %>% select(prof) %>% pull()
var_input_backup <- var_demo_data_profs %>% select(-prof)

```

```{r runMod}

#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")

ocOut.nonseasonal6.list <- c()
Vprog <- Vprog6
for(v in 1:length(pVs)){
  
  Vprog$pV <- pVs[v]
  
  ocOut.nonseasonal6 <- foreach (i = 1:nrow(var_input_backup),
                           .packages = c("dplyr", "tibble")) %dopar% {
                             print(i)
                             
                             var_input_full <- unlist(var_input_backup[i,])
                             
                             App_func(
                               imm_decay_corrected,
                               var_input_full,
                               fix_age_data_full,
                               f_list,
                               # initial state of female population
                               m_list,
                               # initial state of male population
                               TimeStop_dynamics,
                               # 1 year, weekly timestep for demographic component
                               TimeStop_transmission,
                               # 1 day, hourly timestep for transission component
                               output,
                               # model output: tracker or summary stats
                               summary_df,
                               #
                               clean_environment,
                               Vstart,
                               Vprog,
                               fixdata,
                               vardata,
                               birthpeak_w,
                               seasonal
                             )
                           }
  
  
  
  ocOut.nonseasonal6.list[[v]] <- ocOut.nonseasonal6 
}

stopCluster(cl)

```

```{r DynamicsAnalysis}

immDynamics6.clean <- c() # dataframe for expanded immunity dynamics

for(l in 1:length(pVs)){
  dynamics_i <- ocOut.nonseasonal6.list[[l]]
  
  immDynamics6 <- lapply(dynamics_i, select, prop_immune) %>%
  bind_cols() %>%
  t() %>%
  as.data.frame()
  
  colnames(immDynamics6) <- 1:ncol(immDynamics6)
  rownames(immDynamics6) <- 1:nrow(immDynamics6)
  
  immDynamics6.clean <- immDynamics6.clean %>% 
    bind_rows(
      immDynamics6 %>%
        select((t2):ncol(immDynamics6)) %>%
        mutate(prof = profOrder,
               pV = pVs[l])
    )
    
}


immDynamics6.long <- immDynamics6.clean %>%
  gather(key = "weeks", value = "prop_immune", -c(prof, pV)) %>%
  mutate(weeks = as.numeric(weeks))

# Calculate mean and confidence interval
summary_data6 <- immDynamics6.long %>%
  group_by(pV,prof,weeks) %>%
  summarise(
    mean_value = mean(prop_immune),
    lower_ci = quantile(prop_immune, 0.025),
    upper_ci = quantile(prop_immune, 0.975)
  )

plot_immVar6 <- ggplot(summary_data6, aes(x = weeks, y = mean_value)) +
  geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci, fill = factor(pV)), alpha = 0.5) +
  geom_line(aes(col = factor(pV))) +
  geom_hline(yintercept = 0.7, linetype = "dashed")+
  facet_wrap(~prof)+ # facet_grid(pV~prof)+
  guides(fill = "none")+
  labs(x="Time (weeks)", y = "Proportion Immune", col = "pV")+
  coord_cartesian(xlim = c(500,750))

plot_immVar6

filename_dyn <- "OC_nonseasonalDyn_V6m.png"
filename_imm <- "OC_nonseasonalImm_V12m.png"
filename_imm70 <- "OC_nonseasonalImm70_V12m.png"
filename_imm70All <- "OC_nonseasonalImm70All_V12m.png"

if(plotsave){
  ggsave(paste0("plots/applied/",filename_dyn), plot = plot_immVar6, width = 20, height = 10, units = "cm")
  
  }

```


```{r runMod2}

seasonal <- F
## Model Output
output <- "summary_all" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

# validOut = list to store outputs
GSAoutput <- c(); 
ocOut.nonseasonal6Summ <- list()

#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")

ocOut.nonseasonal6Summ.list <- c()


for(v in 1:length(pVs)){
  Vprog$pV <- pVs[v]
  
  summ_i <- foreach (i = 1:nrow(var_input_backup),
                           .packages = c("dplyr", "tibble"),
                           .combine = "rbind") %dopar% {
                             print(i)
                             
                             var_input_full <- unlist(var_input_backup[i,])
                             
                             App_func(
                               imm_decay_corrected,
                               var_input_full,
                               fix_age_data_full,
                               f_list,
                               # initial state of female population
                               m_list,
                               # initial state of male population
                               TimeStop_dynamics,
                               # 1 year, weekly timestep for demographic component
                               TimeStop_transmission,
                               # 1 day, hourly timestep for transission component
                               output,
                               # model output: tracker or summary stats
                               summary_df,
                               #
                               clean_environment,
                               Vstart,
                               Vprog,
                               fixdata,
                               vardata,
                               birthpeak_w,
                               seasonal
                             )
                           }

ocOut.nonseasonal6Summ <- bind_rows(ocOut.nonseasonal6Summ,
                                summ_i %>% mutate(pV = pVs[v],
                                                  prof = profOrder))
}


stopCluster(cl)

```


```{r ocOut.seasonalSumm}

ocOut.summ6df <- ocOut.nonseasonal6Summ %>%
  mutate(prof_group = ifelse(grepl("*shp*", prof), "shp", "goat"),
    prof = factor(
      prof,
      levels = c("oc.goat.aridP","oc.shp.aridP","oc.goat.semiaridP","oc.shp.semiaridP","oc.goat.semiaridM","oc.shp.semiaridM","oc.goat.subhumidM","oc.shp.subhumidM","oc.goat.humidM", "oc.shp.humidM")))

validImm6 <- ocOut.summ6df %>%
  select(tenyr_growth, starts_with("imm"), pV, prof, prof_group) %>%
  gather(key = "stat", value = "value", -c(prof,prof_group, pV)) %>%
  mutate(stat = factor(stat, levels = c("imm_V0", "imm_6m", "imm_12m", "imm70_w", "imm70_wAll", "tenyr_growth" )))

plot_imm6 <- ggplot(validImm6 %>% filter(stat %in% c("imm_V0", "imm_6m", "imm_12m")), 
       aes(x = prof, y = value, group = prof))+ 
    geom_boxplot(alpha = 0.5, aes(fill = prof)) +
    geom_hline(yintercept = 0.7, linetype = "dashed")+
    facet_grid(pV~stat)+
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
          legend.position = "none")+
  scale_fill_brewer(palette = "Dark2")

plot_imm6

plot_imm70.6 <- ggplot(validImm6 %>% filter(stat %in% c("imm70_w")), 
            aes(x = value, y = prof))+ #, col = peakmnth
  geom_boxplot(alpha = 0.5, fill = "grey") +
  geom_vline(xintercept = 26, linetype = "dashed")+
 facet_grid(pV~stat, scales = "free")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "none")
plot_imm70.6

plot_imm70All.6 <- ggplot(validImm6 %>% filter(stat %in% c("imm70_wAll")), 
            aes(x = value, y = prof))+ #, col = peakmnth
  geom_boxplot(alpha = 0.5, fill = "grey")+
 facet_grid(pV~stat, scales = "free")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "none")
plot_imm70All.6

# plot_tenyr6 <- ggplot(validImm6 %>% filter(stat %in% c("tenyr_growth")), 
#             aes(x = prof, y = value))+ # , col = peakmnth
#   geom_boxplot(alpha = 0.5, fill = "grey") +
#   facet_grid(pV~stat, scales = "free")+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
#         legend.position = "none")
# plot_tenyr6

filename_imm6 <- "OC_nonseasonalImm_V6m.png"
filename_imm70.6 <- "OC_nonseasonalImm70_V6m.png"
filename_imm70All.6 <- "OC_nonseasonalImm70All_V6m.png"

if(plotsave){
  ggsave(paste0("plots/applied/",filename_imm6), plot = plot_imm6, width = 10, height = 20, units = "cm")
  ggsave(paste0("plots/applied/",filename_imm70.6), plot = plot_imm70.6, width = 10, height = 10, units = "cm")
  ggsave(paste0("plots/applied/",filename_imm70All.6), plot = plot_imm70All.6, width = 10, height = 10, units = "cm")
  
  }

```