---
title: "cgiar_validation"
author: "Beth Savagar"
date: "2023-11-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup}

applied_example <- F
local <- T

############
## SETUP ##
############

# local filepath: 
if(local){
  filepath <- ""
}else{
  # cluster filepath
  filepath <- "/storage/users/bsavagar/"
}

## Libraries
source(paste0(filepath,"scripts/setup.R")) 

## Functions:
source(paste0(filepath, "functions/Appliedfunc.R")) # wrapper function
source(paste0(filepath, "functions/demos_summary.R")) # summary stats for output
source(paste0(filepath, "functions/dynmod-vac.R")) # flock dynamics model function
source(paste0(filepath, "functions/output.R")) # what to include in output df
source(paste0(filepath, "functions/GSA_outputs.R")) # summary stats accounting for vac
```


```{r loadpars}
## Load parameters
datafile1 <- "-OC_validation"
# load data for Applied-Examples & Applied-LHS
fix_age_data_full <- read_csv(paste0("data/Applied_parameters/state_vars","-OC_validation",".csv"),col_names=T)
var_demo_dataMort <- read_csv(paste0("data/Applied_parameters/demographics","-OC_validationMORT",".csv"), col_names=T)
var_demo_dataOff <- read_csv(paste0("data/Applied_parameters/demographics","-OC_validationOFF",".csv"), col_names=T)
imm_decay_corrected <- read_csv("data/imm_decay_bodjo_v2.csv") 
var_demo_data_backup <- var_demo_data_full
## Datasets
datasets <- fix_age_data_full %>% select(-c(parameter)) %>% colnames()
```

```{r modsetup}
######################
## MODEL SETUP ##
######################

## Simulation:
TimeStop_dynamics <- 2*52 # 2 years only interested in rates for 1 y
TimeStop_transmission <- 24 # 1 day, hourly timestep for transmission component
min_pop <- 1 # set minimum size of population, if pop drops below then set to 0

## Model Output
output <- "mort_only" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)

#######################
## Vaccination Setup ##
#######################
# see applied_vaccination
pV <- 1
source("scripts/applied/applied_vaccination.R")
Vstart <- Vprog %>% filter(Vround==1) %>% pull(Vweek)

##################
## MODEL INPUTS ##
##################

# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

turnover <- F; 
dynamics <- T; 
transmission <- F; 
clean_environment <- T

# timepoints for population growth
t2 <- TimeStop_dynamics/2 # 5 year pop growth
t1 <- TimeStop_dynamics


```


## ALL Mortality Rates

```{r Allmort_target}

##################################
## LHS DEMOGRAPHIC PARS ##
##################################

dataset <- "oc.shp.aridP.mort"
data_filename <- gsub("\\.","",dataset)

lhs <- T
lhs_n <- 1e4 # number of sets (parameter combinations)
pairs_plot <- F
SA <- TRUE

# set seed
set.seed(1) # so that results are consistent

pars_min <- paste0(dataset, ".min") # minimum val
pars_max <-  paste0(dataset, ".max") # maximum val
fixdata <- dataset # set dataset for state_vars
vardata <- dataset


source("scripts/applied/applied_lhs.R") # output var_input_df contains all parameter combinations for uncertain demographics.

if(dataset == "lesnoff.ft"){
  rates <- "wkly"
}else{
  rates <- "yrly"
}

# Format demographic parameter sets:
var_input_backup <- var_input_df %>% as.data.frame()

OutMort <- c()


#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")


################
## SIMULATION ##
################
OutMort <- foreach (i = 1:nrow(var_input_backup), 
                .combine = "rbind",
                .packages = c("dplyr", "tibble")
) %dopar% {
  
  print(i)
  var_input_full <- unlist(var_input_backup[i,])
  
  App_func(
    imm_decay_corrected,
    var_input_full,
    fix_age_data_full,
    f_list, # initial state of female population
    m_list, # initial state of male population
    TimeStop_dynamics, # 1 year, weekly timestep for demographic component
    TimeStop_transmission, # 1 day, hourly timestep for transission component
    output, # model output: tracker or summary stats
    summary_df, #
    clean_environment,
    Vstart,
    Vprog,
    fixdata,
    vardata
  )
}

stopCluster(cl)

```

```{r mort_filter}

OutMort <- as.data.frame(OutMort) %>%
  mutate(set = 1:nrow(.)) %>%
  select(set, mortF06, mortF612,mortF12end, 
         mortM06, mortM612)

OC_target <- read_csv("data/Applied_parameters/target-OC_validation.csv")

rateMin <- "oc.shp.aridP.targ.min"
rateMax <- "oc.shp.aridP.targ.max"

# female mortality <12m target
F1targ_min <- OC_target %>% filter(parameter == "mort1") %>% select(all_of(`rateMin`)) %>% pull()
F1targ_max <- OC_target %>% filter(parameter == "mort1") %>% select(all_of(`rateMax`)) %>% pull()

F2targ_min <- OC_target %>% filter(parameter == "mort2f") %>% select(all_of(`rateMin`)) %>% pull()
F2targ_max <- OC_target %>% filter(parameter == "mort2f") %>% select(all_of(`rateMax`)) %>% pull()

F3targ_min <- OC_target %>% filter(parameter == "mort3f") %>% select(all_of(`rateMin`)) %>% pull()
F3targ_max <- OC_target %>% filter(parameter == "mort3f") %>% select(all_of(`rateMax`)) %>% pull()

# Male mort <12m target
M1targ_min <- OC_target %>% filter(parameter == "mort1") %>% select(all_of(`rateMin`)) %>% pull()
M1targ_max <- OC_target %>% filter(parameter == "mort1") %>% select(all_of(`rateMax`)) %>% pull()

M2targ_min <- OC_target %>% filter(parameter == "mort2m") %>% select(all_of(`rateMin`)) %>% pull()
M2targ_max <- OC_target %>% filter(parameter == "mort2m") %>% select(all_of(`rateMax`)) %>% pull()

OutMort %>% 
  filter(mortF06 >=F1targ_min &
         mortF06<=F1targ_max)

mortTarg <- OutMort %>% 
  mutate(mortF1_targ = ifelse(mortF06>=F1targ_min & mortF06<=F1targ_max, 1, 0),
         mortF2_targ = ifelse(mortF612>=F2targ_min & mortF612<=F2targ_max, 1, 0),
         mortF3_targ = ifelse(mortF12end>=F3targ_min & mortF12end<=F3targ_max, 1, 0),
         mortM1_targ = ifelse(mortM06>=M1targ_min & mortM06<=M1targ_max, 1, 0),
         mortM2_targ = ifelse(mortM612>=M2targ_min & mortM612<=M2targ_max, 1, 0)) %>%
  mutate(targSum = apply(.[7:11],1,sum))



validAll <- mortTarg %>% filter(targSum == 5) %>% pull(set)
validMort <- var_input_backup[validAll, ] %>% select(mortality_y, mortality_a)

summary(validMort) %>% kable()

ggplot(validMort, aes(x=mortality_y, y = mortality_a))+
  geom_point()+
  theme_bw()

valid_mortFM_long <- validMort %>% gather(key = "par", value = "value")
ggplot(valid_mortFM_long, aes(x = par, y = value))+
  geom_boxplot()+
  theme_bw()


```

## Conditions on Mortality Parameter sets:
- For all mortality parameter sets they must also satisfy the condition that youth mortality is greater than adult mortality (`mortality_y`>>`mortality_a`)


## ALL Offtake Rates

```{r modsetup}
######################
## MODEL SETUP ##
######################

## Simulation:
TimeStop_dynamics <- 2*52 # 2 years only interested in rates for 1 y
TimeStop_transmission <- 24 # 1 day, hourly timestep for transmission component
min_pop <- 1 # set minimum size of population, if pop drops below then set to 0

## Model Output
output <- "off_only" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)

#######################
## Vaccination Setup ##
#######################
# see applied_vaccination
pV <- 1
source("scripts/applied/applied_vaccination.R")
Vstart <- Vprog %>% filter(Vround==1) %>% pull(Vweek)

##################
## MODEL INPUTS ##
##################

# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

turnover <- F; 
dynamics <- T; 
transmission <- F; 
clean_environment <- T

# timepoints for population growth
t2 <- TimeStop_dynamics/2 # 5 year pop growth
t1 <- TimeStop_dynamics


```


```{r Alloff_target}

##################################
## LHS DEMOGRAPHIC PARS ##
##################################

dataset <- "oc.shp.aridP"
data_filename <- gsub("\\.","",dataset)

lhs <- T
lhs_n <- 1e4 # number of sets (parameter combinations)
lhs_n<- 100
pairs_plot <- F
SA <- TRUE

# set seed
set.seed(1) # so that results are consistent

if(output == "off_only"){
  var_demo_data_full <- var_demo_dataOff
}


pars_min <- paste0(dataset, ".min") # minimum val
pars_max <-  paste0(dataset, ".max") # maximum val
fixdata <- dataset # set dataset for state_vars
vardata <- dataset

source("scripts/applied/applied_lhs.R") # output var_input_df contains all parameter combinations for uncertain demographics.

if(dataset == "lesnoff.ft"){
  rates <- "wkly"
}else{
  rates <- "yrly"
}

# Format demographic parameter sets:
var_input_backup <- var_input_df %>% as.data.frame()

OutOff <- c()


#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")


################
## SIMULATION ##
################
OutOff <- foreach (i = 1:nrow(var_input_backup), 
                .combine = "rbind",
                .packages = c("dplyr", "tibble")
) %dopar% {
  
  print(i)
  var_input_full <- unlist(var_input_backup[i,])
  
  App_func(
    imm_decay_corrected,
    var_input_full,
    fix_age_data_full,
    f_list, # initial state of female population
    m_list, # initial state of male population
    TimeStop_dynamics, # 1 year, weekly timestep for demographic component
    TimeStop_transmission, # 1 day, hourly timestep for transission component
    output, # model output: tracker or summary stats
    summary_df, #
    clean_environment,
    Vstart,
    Vprog,
    fixdata,
    vardata
  )
}

stopCluster(cl)

```

```{r off_filter}

OutOff <- as.data.frame(OutOff) %>%
  mutate(set = 1:nrow(.)) %>%
  select(set, offF06, offF612,offF12end, 
         offM06, offM612, offAll)

OC_target <- read_csv("data/Applied_parameters/target-OC_validation.csv")

rateMin <- "oc.shp.aridP.targ.min"
rateMax <- "oc.shp.aridP.targ.max"

# female mortality <12m target
targ_min <- OC_target %>% filter(parameter == "Off_all") %>% select(all_of(`rateMin`)) %>% pull()
targ_max <- OC_target %>% filter(parameter == "Off_all") %>% select(all_of(`rateMax`)) %>% pull()

offTarg <- OutOff %>% 
  mutate(off_targ = ifelse(offAll>=targ_min & offAll<=targ_max, 1, 0))

var_input_backup

summary(var_input_backup %>% select(starts_with("NET"))) %>% kable()

```


## Conditions on Offtake Parameter sets:
- For all offtake parameter sets they must also satisfy the condition that Young male offtake (off_m2) is higher than female offtake (off_f)


## VALID OFF LOOP: 

```{r validloop}


lhs_n <- 10000
## Model Output
output <- "off_only" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

# validOut = list to store outputs
GSAoutput <- c(); 
outOffls <- list()
offValidParsls <- list()

#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")


#####################
## LOOP ##
#####################

for(d in 1:length(datasets)){
  dataset <- datasets[d]
  
  ##################################
  ## LHS DEMOGRAPHIC PARS ##
  ##################################
  
  data_filename <- gsub("\\.", "", dataset)
  
  if (dataset == "lesnoff.ft") {
    rates <- "wkly"
  } else{
    rates <- "yrly"
  }
  
  # set seed
  set.seed(1) # so that results are consistent
  
  pars_min <- paste0(dataset, ".min") # minimum val
  pars_max <-  paste0(dataset, ".max") # maximum val
  fixdata <- dataset # set dataset for state_vars
  vardata <- dataset
  
  source("scripts/applied/applied_lhs.R") # output var_input_df contains all parameter combinations for uncertain demographics.
  
  
  # Format demographic parameter sets:
  var_input_backup <- var_input_df %>% as.data.frame()
  
  ################
  ## SIMULATION ##
  ################
  OutOff <- foreach (i = 1:nrow(var_input_backup),
                          .packages = c("dplyr", "tibble"),
                          .combine = "rbind") %dopar% {
                            print(i)
                            
                            var_input_full <- unlist(var_input_backup[i, ])
                            
                            App_func(
                              imm_decay_corrected,
                              var_input_full,
                              fix_age_data_full,
                              f_list,# initial state of female population
                              m_list, # initial state of male population
                              TimeStop_dynamics,# 1 year, weekly timestep for demographic component
                              TimeStop_transmission, # 1 day, hourly timestep for transission component
                              output,# model output: tracker or summary stats
                              summary_df, #
                              clean_environment,
                              Vstart,
                              Vprog,
                              fixdata,
                              vardata
                            )
                          }
  
  OutOff <- as.data.frame(OutOff) %>%
    mutate(set = 1:nrow(.)) %>%
    select(set, offF06, offF612,offF12end, 
           offM06, offM612, offAll)
  
  rateMin <- paste0(dataset,".targ.min")
  rateMax <-  paste0(dataset,".targ.max")
  
  # female mortality <12m target
  targ_min <- OC_target %>% filter(parameter == "Off_all") %>% select(all_of(`rateMin`)) %>% pull()
  targ_max <- OC_target %>% filter(parameter == "Off_all") %>% select(all_of(`rateMax`)) %>% pull()
  
  offTarg <- OutOff %>% mutate(off_targ = ifelse(offAll>=targ_min & offAll<=targ_max, 1, 0))
  outOffls[[d]] <- offTarg
  
  offValidIDs <- offTarg %>% filter(off_targ==1) %>% pull(set)
  offValidPars <- var_input_backup[offValidIDs, ]
  offValidParsls[[d]] <- offValidPars
}

```

## 







## VALID MORT LOOP

```{r validMortLoop}

lhs_n <- 10000
## Model Output
output <- "mort_only" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

# validOut = list to store outputs
GSAoutput <- c(); 
outMortls <- list()
mortValidParsls <- list()

#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")


#####################
## LOOP ##
#####################

for(d in 1:length(datasets)){
  dataset <- datasets[d]
  
  ##################################
  ## LHS DEMOGRAPHIC PARS ##
  ##################################
  
  data_filename <- gsub("\\.", "", dataset)
  
  if (dataset == "lesnoff.ft") {
    rates <- "wkly"
  } else{
    rates <- "yrly"
  }
  
  # set seed
  set.seed(1) # so that results are consistent
  
  pars_min <- paste0(dataset, ".min") # minimum val
  pars_max <-  paste0(dataset, ".max") # maximum val
  fixdata <- dataset # set dataset for state_vars
  vardata <- dataset
  
  source("scripts/applied/applied_lhs.R") # output var_input_df contains all parameter combinations for uncertain demographics.
  
  
  # Format demographic parameter sets:
  var_input_backup <- var_input_df %>% as.data.frame()
  
  ################
  ## SIMULATION ##
  ################
  OutMort <- foreach (i = 1:nrow(var_input_backup),
                     .packages = c("dplyr", "tibble"),
                     .combine = "rbind") %dopar% {
                       print(i)
                       
                       var_input_full <- unlist(var_input_backup[i, ])
                       
                       App_func(
                         imm_decay_corrected,
                         var_input_full,
                         fix_age_data_full,
                         f_list,# initial state of female population
                         m_list, # initial state of male population
                         TimeStop_dynamics,# 1 year, weekly timestep for demographic component
                         TimeStop_transmission, # 1 day, hourly timestep for transission component
                         output,# model output: tracker or summary stats
                         summary_df, #
                         clean_environment,
                         Vstart,
                         Vprog,
                         fixdata,
                         vardata
                       )
                     }
  
  OutMort <- as.data.frame(OutMort) %>%
    mutate(set = 1:nrow(.)) %>%
    select(set, mortF06, mortF612,mortF12end, 
           mortM06, mortM612)
  
  rateMin <- paste0(dataset,".targ.min")
  rateMax <-  paste0(dataset,".targ.max")
  
  
  # female mortality <12m target
  F1targ_min <- OC_target %>% filter(parameter == "mort1") %>% select(all_of(`rateMin`)) %>% pull()
  F1targ_max <- OC_target %>% filter(parameter == "mort1") %>% select(all_of(`rateMax`)) %>% pull()
  
  F2targ_min <- OC_target %>% filter(parameter == "mort2f") %>% select(all_of(`rateMin`)) %>% pull()
  F2targ_max <- OC_target %>% filter(parameter == "mort2f") %>% select(all_of(`rateMax`)) %>% pull()
  
  F3targ_min <- OC_target %>% filter(parameter == "mort3f") %>% select(all_of(`rateMin`)) %>% pull()
  F3targ_max <- OC_target %>% filter(parameter == "mort3f") %>% select(all_of(`rateMax`)) %>% pull()
  
  # Male mort <12m target
  M1targ_min <- OC_target %>% filter(parameter == "mort1") %>% select(all_of(`rateMin`)) %>% pull()
  M1targ_max <- OC_target %>% filter(parameter == "mort1") %>% select(all_of(`rateMax`)) %>% pull()
  
  M2targ_min <- OC_target %>% filter(parameter == "mort2m") %>% select(all_of(`rateMin`)) %>% pull()
  M2targ_max <- OC_target %>% filter(parameter == "mort2m") %>% select(all_of(`rateMax`)) %>% pull()
  
  
  mortTarg <- OutMort %>% 
    mutate(mortF1_targ = ifelse(mortF06>=F1targ_min & mortF06<=F1targ_max, 1, 0),
           mortF2_targ = ifelse(mortF612>=F2targ_min & mortF612<=F2targ_max, 1, 0),
           mortF3_targ = ifelse(mortF12end>=F3targ_min & mortF12end<=F3targ_max, 1, 0),
           mortM1_targ = ifelse(mortM06>=M1targ_min & mortM06<=M1targ_max, 1, 0),
           mortM2_targ = ifelse(mortM612>=M2targ_min & mortM612<=M2targ_max, 1, 0)) %>%
    mutate(targSum = apply(.[7:11],1,sum))
  
  outMortls[[d]] <- mortTarg
  
  mortValidIDs <- mortTarg %>% filter(targSum==5) %>% pull(set)
  mortValidPars <- var_input_backup[mortValidIDs, ] # %>% select(mortality_y, mortality_a)
  mortValidParsls[[d]] <- mortValidPars
}

```

```{r}




```


## Valid parameter combinations?

```{r lesnoffInput}

# exclude offtake where young offtake is very high
valid_offFM_test <- valid_offFM_df %>% filter(NET_offtake_y < NET_offtake_f)
valid_mortFM_df 

# Use valid offtake and mortality parameters to produce dataframe of parameter inputs for lesnoff testing
# var_input_lesnoff <- valid_mortFM_df %>%
#   cbind(valid_offFM_test %>% slice(rep(1:n(), each = nrow(valid_mortFM_df))))
# 
# setdiff(colnames(var_input_backup),colnames(var_input_lesnoff))
# 
# var_input_lesnoff <- var_input_lesnoff %>%
#   mutate("adu_f_max_yrs" = 9,
#          "adu_m_max_yrs" = 4,
#          "min_age_offtake" = 6,
#          "min_age_repro" = 9, 
#          "birth_rate" = 0.9365096)
# 
# write.csv(var_input_lesnoff, file = "data/Applied_parameters/demographics-lesnoff_input.csv", row.names = F)

var_input_lesnoff <- read_csv("data/Applied_parameters/demographics-lesnoff_input.csv")

```


```{r lesnoffMod}

######################
## MODEL SETUP ##
######################

## Simulation:
TimeStop_dynamics <- 20*52 # 2 years only interested in rates for 1 y
TimeStop_transmission <- 24 # 1 day, hourly timestep for transmission component
min_pop <- 1 # set minimum size of population, if pop drops below then set to 0

#######################
## Vaccination Setup ##
#######################
# see applied_vaccination
pV <- 1
source("scripts/applied/applied_vaccination.R")
Vstart <- Vprog %>% filter(Vround==1) %>% pull(Vweek)

##################
## MODEL INPUTS ##
##################

## Model Output
output <- "summary_all" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

turnover <- F; 
dynamics <- T; 
transmission <- F; 
clean_environment <- T

# timepoints for population growth
t2 <- TimeStop_dynamics/2 # 5 year pop growth
t1 <- TimeStop_dynamics


##################################
## LHS DEMOGRAPHIC PARS ##
##################################

dataset <- "lesnoff.yr" # for selecting state_vars input data
data_filename <- gsub("\\.","",dataset)

lhs <- T
# lhs_n <- 1 # number of sets (parameter combinations)
# pairs_plot <- F
# SA <- TRUE
# 
# # set seed
# set.seed(1) # so that results are consistent
# 
# pars_min <- paste0(dataset, ".min") # minimum val
# pars_max <-  paste0(dataset, ".max") # maximum val
# fixdata <- dataset # set dataset for state_vars
# vardata <- dataset
# 
# 
# source("scripts/applied/applied_lhs.R") # output var_input_df contains all parameter combinations for uncertain demographics.

if(dataset == "lesnoff.ft"){
  rates <- "wkly"
}else{
  rates <- "yrly"
}

# Format demographic parameter sets:
var_input_backup <- var_input_lesnoff %>% as.data.frame()

Out_lesnoff <- c()


#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")


################
## SIMULATION ##
################
Out_lesnoff <- foreach (i = 1:nrow(var_input_backup), 
                .packages = c("dplyr", "tibble"),
                .combine = "rbind"
) %dopar% {
  
  print(i)
  var_input_full <- unlist(var_input_backup[i,])
  
  App_func(
    imm_decay_corrected,
    var_input_full,
    fix_age_data_full,
    f_list, # initial state of female population
    m_list, # initial state of male population
    TimeStop_dynamics, # 1 year, weekly timestep for demographic component
    TimeStop_transmission, # 1 day, hourly timestep for transission component
    output, # model output: tracker or summary stats
    summary_df, #
    clean_environment,
    Vstart,
    Vprog,
    fixdata,
    vardata
  )
}

stopCluster(cl)

```

```{r lesnoffGrowth}

# Out_lesnoff is a dataframe of summary data for each parameter set "valid" parameter set

## Plot population growth stats: 
# - Total Growth (20y), 
# - Midyr Growth (10y), 
# - Finyr Growth (1y)

## POPULATION GROWTH ## 

# Long dataframe:
popgrowth <- Out_lesnoff %>% 
  select(ends_with("growth")) %>% 
  gather(key = "par", value = "prop") %>% 
  mutate(par = factor(par, levels = c("finyr_growth", "tenyr_growth", "pop_growth")))

Out_lesnoff %>% select(ends_with("growth")) %>% summary()

# Boxplot of growth statistics:
growth_summplot <- ggplot(popgrowth, aes(x=par, y = prop))+
  geom_boxplot()+
  facet_wrap(~par, scales = "free_x")+
  labs(x = "Growth Stat", 
       y = "Pop Growth",
       title = "Growth statistics for Lesnoff data, LHS parameter sets")+
  theme_bw()

growth_summplot

# Boxplot of Final year growth: 
finyr_summplot <- ggplot(Out_lesnoff, aes(finyr_growth))+
  geom_histogram(colour = "black",
                 alpha = 0.5)+
  geom_vline(xintercept = 1)+
  labs(x="Final year growth", 
       y = "Count", 
       title = "Distribution of final year growth, Lesnoff, (LHS parameter sets)")+
  theme_bw()

finyr_summplot


## AGE-SEX DYNAMICS ##

# Long dataframe:
agesex <- Out %>% 
  select(starts_with("pf"), starts_with("pm")) %>% 
  gather(key = "par", value = "prop")

# Boxplot of stable age-sex structure:
agesex_summplot <- ggplot(agesex, aes(x=par, y = prop))+
  geom_boxplot(fill = "grey", 
               alpha = 0.5)+
  labs(x="Age-Sex Group", 
       y = "Proportion",
       title = "Stable Age-Sex structure, Lesnoff, (LHS parameter sets)")+
  theme_bw()
  
agesex_summplot
agesex %>% group_by(par) %>% summarise(meanprop = mean(prop)) %>% kable()

# All growth plots:
ggarrange(growth_summplot, finyr_summplot, agesex_summplot, ncol = 1)

```

```{r lesnoffOutValid}

#------------------------------------------------------------------------------
## VALID RESULTS ##

##################################
## Valid Age-Sex Conditions ##
##################################

## Min and max proportions for each sex-age group (see age-sex SS)
pfKid.min <- 0.05; pfKid.max <- 0.19
pfSub.min <- 0.06; pfSub.max <- 0.19
pfAdu.min <- 0.21; pfAdu.max <- 0.62

pmKid.min <- 0.05; pmKid.max <- 0.16
pmSub.min <- 0.04; pmSub.max <- 0.15
pmAdu.min <- 0.01; pmAdu.max <- 0.15
  

#########################################################
# Retain behavioral parameter sets
#########################################################

# add set id to output df:
Out_lesnoff <- Out_lesnoff %>%
  mutate(set = 1:nrow(Out_lesnoff), 
         midyr_growth = tenyr_growth)

# Edit Out to contain identifier variables for pop growth (5%,15%) and pop growth with age-sex structure 
Out_ext <- Out_lesnoff %>%
  mutate(midyr_growth = replace_na(midyr_growth, 0),
         # add variables to identify parameter sets with growth between 5% and 15%
         midyr_15 = ifelse(midyr_growth>=0.85 & midyr_growth <=1.15, 1, 0),
         midyr_05 = ifelse(midyr_growth>=0.95 & midyr_growth <=1.05, 1, 0)) %>%
  
  # add variables to identify parameter sets with growth between 5% and 15% AND age-sex conditions
  mutate(
    midyr_15age = ifelse(
      midyr_15 == 1 &
        pfKid >= pfKid.min & pfKid <= pfKid.max &
        pfSub >= pfSub.min & pfSub <= pfSub.max &
        pfAdu >= pfAdu.min & pfAdu <= pfAdu.max &
        
        pmKid >= pmKid.min & pmKid <= pmKid.max &
        pmSub >= pmSub.min & pmSub <= pmSub.max &
        pmAdu >= pmAdu.min & pmAdu <= pmAdu.max,1,0),
    
    midyr_05age = ifelse(
      midyr_05 == 1 &
        pfKid >= pfKid.min & pfKid <= pfKid.max &
        pfSub >= pfSub.min & pfSub <= pfSub.max &
        pfAdu >= pfAdu.min & pfAdu <= pfAdu.max &
        
        pmKid >= pmKid.min & pmKid <= pmKid.max &
        pmSub >= pmSub.min & pmSub <= pmSub.max &
        pmAdu >= pmAdu.min & pmAdu <= pmAdu.max,1,0)
  )

Out_ext %>% group_by(midyr_15age, midyr_05age) %>% count() %>% kable()

##################
## Valid Output ##
##################

Out_valid <- Out_ext %>%
  filter(midyr_15age == 1 |
           midyr_05age == 1)

## Refine parameter dataframe:
Out_parameters <- var_input_backup %>%
  mutate(set = 1:nrow(var_input_backup)) %>%
  left_join(Out_ext %>%
              select(midyr_growth,
                     midyr_15,
                     midyr_05,
                     midyr_15age,
                     midyr_05age,
                     set), by = c("set"))

pars_valid <- Out_parameters %>% 
  filter(midyr_15age == 1 |
           midyr_05age == 1)  %>%
  select(-c(midyr_15,
            midyr_05,
            set))

library(GGally)
pairs(pars_valid %>% select(-c(midyr_growth,midyr_05age,midyr_15age)))

```


```{r lesnoffMod}

######################
## MODEL SETUP ##
######################

## Simulation:
TimeStop_dynamics <- 10*52 # 2 years only interested in rates for 1 y
TimeStop_transmission <- 24 # 1 day, hourly timestep for transmission component
min_pop <- 1 # set minimum size of population, if pop drops below then set to 0

#######################
## Vaccination Setup ##
#######################
# see applied_vaccination
pV <- 1
source("scripts/applied/applied_vaccination.R")
Vstart <- Vprog %>% filter(Vround==1) %>% pull(Vweek)

##################
## MODEL INPUTS ##
##################

## Model Output
output <- "dynamics" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

turnover <- F; 
dynamics <- T; 
transmission <- F; 
clean_environment <- T

# timepoints for population growth
t2 <- TimeStop_dynamics/2 # 5 year pop growth
t1 <- TimeStop_dynamics


##################################
## LHS DEMOGRAPHIC PARS ##
##################################

dataset <- "lesnoff.yr" # for selecting state_vars input data
data_filename <- gsub("\\.","",dataset)

lhs <- T
# lhs_n <- 1 # number of sets (parameter combinations)
# pairs_plot <- F
# SA <- TRUE
# 
# # set seed
# set.seed(1) # so that results are consistent
# 
# pars_min <- paste0(dataset, ".min") # minimum val
# pars_max <-  paste0(dataset, ".max") # maximum val
# fixdata <- dataset # set dataset for state_vars
# vardata <- dataset
# 
# 
# source("scripts/applied/applied_lhs.R") # output var_input_df contains all parameter combinations for uncertain demographics.

if(dataset == "lesnoff.ft"){
  rates <- "wkly"
}else{
  rates <- "yrly"
}

# Format demographic parameter sets:
var_input_backup <- var_input_lesnoff %>% as.data.frame()

Out_lesnoffDyn <- c()


#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")


################
## SIMULATION ##
################
Out_lesnoffDyn <- foreach (i = 1:nrow(var_input_backup), 
                .packages = c("dplyr", "tibble")
) %dopar% {
  
  print(i)
  var_input_full <- unlist(var_input_backup[i,])
  
  App_func(
    imm_decay_corrected,
    var_input_full,
    fix_age_data_full,
    f_list, # initial state of female population
    m_list, # initial state of male population
    TimeStop_dynamics, # 1 year, weekly timestep for demographic component
    TimeStop_transmission, # 1 day, hourly timestep for transission component
    output, # model output: tracker or summary stats
    summary_df, #
    clean_environment,
    Vstart,
    Vprog,
    fixdata,
    vardata
  )
}

stopCluster(cl)

```


```{r}


################################
## POP & AGE-SEX DYNAMICS ##
################################

# Out is a list of df which track full population dynamics for 1000 (lhs_n) parameter combinations over 20y periods

# Sample for plotting
dyn_sample <- sample(1:nrow(var_input_lesnoff), 10, replace = F)

# Transform Out (list) into a df of dynamics with each set identified:
Out_dynamics <- Out_lesnoffDyn %>%
  do.call(rbind, .) %>% 
  mutate(set = rep(1:nrow(var_input_lesnoff), each = TimeStop_dynamics))

# Population Growth plot:
growth_dynplot <- ggplot(Out_dynamics, 
       aes(x = w, y = sum_pop, group = set)) + 
  labs(x="weeks", 
       y = "Population Size",
       title = "Population growth over 10 years, Lesnoff, (LHS Valid Sets)")+
  geom_line()+
  theme_bw()

# AgeSex Dynamics df: 
Out_agesex <- Out_dynamics %>% 
  select(c("w", "set", starts_with("pf"), starts_with("pm"))) %>% 
  gather(key = "par", value = value, -c(w,set)) %>%
  mutate(par = factor(par, levels = c("pfAdu", "pfSub", "pfKid", 
                                         "pmAdu","pmSub","pmKid",
                                         "pF")))

Out_agesex %>% filter(w == max(w)) %>% group_by(par) %>% summarise(meanProp = mean(value)) %>% kable()

# Age-Sex Plot:
agesex_dynplot <- ggplot(Out_agesex, 
       aes(x = w, y = value, group = set, col = par)) + 
  geom_line()+
  facet_wrap(~par)+
  labs(x="Weeks", 
       y = "Proportion",
       title = "Age-Sex dynamics, Lesnoff, (LHS Parameter Sets)")+
  theme_bw()

growth_dynplot
agesex_dynplot
ggarrange(growth_dynplot, agesex_dynplot, ncol = 1)


## twoyr growth
twoyr_growth <- sapply(Out_lesnoffDyn, function(x)
  x[nrow(x),"sum_pop"] / x[(nrow(x)-(2*52)), "sum_pop"]
)

OutL2 <- Out_lesnoff %>%
  mutate(twoyr_growth = replace_na(twoyr_growth, 0))

twoyr_summplot <- ggplot(OutL2, aes(twoyr_growth))+
  geom_histogram(colour = "black",
                 alpha = 0.5)+
  geom_vline(xintercept = 1)+
  labs(x="Two year growth", 
       y = "Count", 
       title = "Distribution of final TWO year growth, Lesnoff, (LHS parameter sets)")+
  theme_bw()

twoyr_boxplot <- ggplot(OutL2, aes(y = twoyr_growth))+
  geom_boxplot()+
  labs(x= "", 
       y = "Two year growth", 
       title = "Final TWO year growth, Lesnoff, (LHS parameter sets)")+
  theme_bw()

twoyr_summplot

twoyr_boxplot

ggarrange(twoyr_summplot, twoyr_boxplot, ncol = 1)

summary(OutL2 %>% filter(twoyr_growth>0) %>% select(twoyr_growth)) %>% kable()


twoyr_min <- 0.922
twoyr_max <- 1.172

length(which(twoyr_growth >= twoyr_min & twoyr_growth <= twoyr_max))

OutL2 %>% filter(twoyr_growth >= twoyr_min & twoyr_growth <= twoyr_max)
L2_valid <- OutL2 %>% filter(twoyr_growth >= twoyr_min & twoyr_growth <= twoyr_max) %>% pull(set)
var_input_lesnoffv2 <- var_input_lesnoff[L2_valid, ]

# write.csv(var_input_lesnoffv2, file = "data/Applied_parameters/demographics-lesnoff_input2.csv", row.names = F)
```


```{r ranges}
# how to valid parameters fit in the RSA GSA range

RSApars <- read_csv(paste0("data/Applied_parameters/demographics","-lesnoff_check",".csv"), col_names=T) %>%
  select(RSA.min, RSA.max, parameter)

RSAranges <- RSApars %>% 
  select(parameter,
         RSA.min,
         RSA.max) %>% 
  gather(key = "datasource", value = "value", -parameter) %>%
  mutate(datasource = gsub("\\.min|\\.max","", datasource))

# ANALYSIS OF LESNOFF LHS PARAMETER SETS:

lesnoff_ranges <- var_input_lesnoff[L2_valid,] %>% 
  t() %>%
  as.data.frame() %>%
  mutate(min = apply(.,1,min),
         max = apply(.,1,max), 
         par = rownames(.)) %>%
  select(par,min,max) %>%
  gather(key = "key", value = "value", -par) %>%
  mutate(datasource = "lesnoff") %>%
  select(parameter = par, datasource, value) %>%
  rbind(RSAranges)

p1<- ggplot(lesnoff_ranges %>% filter(parameter %in% c("adu_f_max_yrs", "adu_m_max_yrs","min_age_offtake","min_age_repro")), aes(x=parameter, y=value, col = datasource))+
  geom_point(position=position_dodge(width=0.2))+
  geom_line(size = 1, position=position_dodge(width=0.2))+
  labs(x = "Parameter")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
        legend.position = "none",
        text = element_text(size=16))

p2 <- ggplot(lesnoff_ranges %>% filter(!parameter %in% c("adu_f_max_yrs", "adu_m_max_yrs","min_age_offtake","min_age_repro", "ppr_mortality_y", "ppr_mortality_a")), 
       aes(x=parameter, y=value, col = datasource))+
  geom_point(position=position_dodge(width=0.2))+
  geom_line(size = 1, position=position_dodge(width=0.2))+
  labs(x = "Parameter")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
        text = element_text(size=16))

ggarrange(p1,p2)


```
