---
title: "validvac_seasonalFixed"
author: "Beth Savagar"
date: "2023-12-11"
output: html_document
---

# SEASONAL OC

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library}
# libraries not accounted for in setup script
library(GGally)
plotsave <- F
custom_theme <- theme_bw() + theme(text = element_text(family = "Times New Roman", size = 9))
theme_set(custom_theme)
custom_palette <- c("#004D40", "#00695C", "#00796B", "#00897B", "#009688", "#4A148C", "#6A1B9A", "#7B1FA2", "#8E24AA", "#9C27B0")

```

```{r modSetup1}
############
## SETUP ##
############
local <- T
# local filepath: 
if(local){
  filepath <- ""
}else{
  # cluster filepath
  filepath <- "/storage/users/bsavagar/"
}

## Libraries
source(paste0(filepath,"scripts/setup.R")) 

## Functions:
source(paste0(filepath, "functions/Appliedfunc_seasonalfixed.R")) # wrapper function
source(paste0(filepath, "functions/demos_summary.R")) # summary stats for output
source(paste0(filepath, "functions/dynmod-vac_seasonalfixed.R")) # flock dynamics model function
source(paste0(filepath, "functions/output.R")) # what to include in output df
source(paste0(filepath, "functions/GSA_outputs.R")) # summary stats accounting for vac

```


```{r selectData}
# 9/11/23: Run model with LHS of oc parameter space. Analyse results against original valid population conditions and against oc population growth reports. 

applied_example <- T

## Load parameters
datafile <- "-OC_validPars-seasonal"
fix_age_data_full <- read_csv(paste0("data/Applied_parameters/state_vars",datafile,".csv"),col_names=T)
var_demo_data_full <- read_csv(paste0("output/Applied/applied_outValidPars_OC_2023-12-05.csv"))
var_demo_data_full <- read_csv(paste0("output/Applied/applied_outValidPars_OC_2023-12-11.csv"))
# load mean annual birth rate (calc from validVac non-seasonal.Rmd)
nBirths_df <- read_csv("output/Applied/stableAgeSex/Applied_nBirths_OC.csv")
imm_decay_corrected <- read_csv("data/imm_decay_bodjo_v2.csv") 

## Datasets
datasets <- fix_age_data_full %>% select(-parameter) %>% colnames()
#combine nBirths with other demogrpahics
var_demo_data_full <- var_demo_data_full %>%
  mutate(nBirths_yr = nBirths_df$mean)

```

```{r modSetup2}

######################
## MODEL SETUP ##
######################

## Simulation:
TimeStop_dynamics <- 20*52 # 2 years only interested in rates for 1 y
TimeStop_transmission <- 24 # 1 day, hourly timestep for transmission component
min_pop <- 1 # set minimum size of population, if pop drops below then set to 0

#######################
## Vaccination Setup ##
#######################
# see applied_vaccination
pV <- 1
source("scripts/applied/applied_vaccination.R")
Vstart <- Vprog %>% filter(Vround==1) %>% pull(Vweek)

##################
## RUN MODEL ##
##################

turnover <- F; 
dynamics <- T; 
transmission <- F; 
clean_environment <- T
seasonal <- T

# timepoints for population growth
t2 <- TimeStop_dynamics/2 # 5 year pop growth
t1 <- TimeStop_dynamics


##################################
## BIRTH PEAKS  ##
##################################

# id which week of the year each month starts on:
wkmnthids <- data.frame(
  mnth = 1:12,
  mnthwk = seq(1,53, by = 4.345) %>% round()
)

peakmnth <- 3  # Month of peak
peakstart <- wkmnthids %>% filter(mnth == peakmnth) %>% pull()
pkwk1 <- seq(from=peakstart, by=1, length.out=4)
birthpeak_w <- c()
time_yrs <- TimeStop_dynamics/52
for(i in 1:time_yrs-1){
  seqjump <- i*52
  pkwki <- pkwk1+seqjump
  birthpeak_w <- c(birthpeak_w,pkwki)
}

##################################
## LHS SETUP  ##
##################################

lhs <- F
lhs_n <- 0 # number of sets (parameter combinations)
pairs_plot <- F
SA <- F

```

# Test implementation of births with 1 example from OC dataset

```{r ocSeasonal}

###################
## MODEL OUTPUT ##
###################

## Model Output
output <- "dynamics" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

# validOut = list to store outputs
GSAoutput <- c(); 
ocOut.seasonal <- list()


#####################
## DATA SELECTION ##
#####################

dataset <- datasets

if (dataset == "lesnoff.ft") {
  rates <- "wkly"
} else{
  rates <- "yrly"
}

fixdata <- dataset # set dataset for state_vars
vardata <- dataset
  
if(lhs){
  source("scripts/applied/applied_lhs.R") # output var_input_df contains all parameter combinations for uncertain demographics.
}

profOrder <- var_demo_data_full %>% select(prof) %>% pull()
var_input_backup <- var_demo_data_full %>% select(-prof)

#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")
  
  ##########################################
  ## SIMULATION - TEST 1 EXAMPLE ##
  ##########################################

var_input_full <- unlist(var_input_backup[1, ])

                                  
ocOut.seasonal <- App_func(
                  imm_decay_corrected,
                  var_input_full,
                  fix_age_data_full,
                  f_list,# initial state of female population
                  m_list, # initial state of male population
                  TimeStop_dynamics,# 1 year, weekly timestep for demographic component
                  TimeStop_transmission, # 1 day, hourly timestep for transission component
                  output,# model output: tracker or summary stats
                  summary_df, #
                  clean_environment,
                  Vstart,
                  Vprog,
                  fixdata,
                  vardata,
                  birthpeak_w,
                  seasonal
                )
                                
  
stopCluster(cl)

```

```{r ocConstant}

seasonal <- F                        
ocOut.constant <- App_func(
                  imm_decay_corrected,
                  var_input_full,
                  fix_age_data_full,
                  f_list,# initial state of female population
                  m_list, # initial state of male population
                  TimeStop_dynamics,# 1 year, weekly timestep for demographic component
                  TimeStop_transmission, # 1 day, hourly timestep for transission component
                  output,# model output: tracker or summary stats
                  summary_df, #
                  clean_environment,
                  Vstart,
                  Vprog,
                  fixdata,
                  vardata,
                  birthpeak_w,
                  seasonal
                )

```

# Review whether population dynamics fluctuate around same average between seasonal and non-seasonal
```{r ocComparison}

ocOut.comparison <- bind_rows(ocOut.constant %>% select(w, sum_pop, prop_immune) %>% mutate(id = "constant"),
                   ocOut.seasonal %>% select(w, sum_pop, prop_immune) %>% mutate(id = "seasonal"))



# Check births are implemented at peak times as intended: 
startpos <- which(c(TRUE, diff(birthpeak_w) > 1))
endpos <- c(startpos[-1] - 1, length(birthpeak_w))
peakrect <- data.frame(startpeak = birthpeak_w[startpos],
                      endpeak = birthpeak_w[endpos])

ggplot() +
  geom_rect(
   data = peakrect,
    aes(
      xmin = startpeak,
      xmax = endpeak,
      ymin = -Inf,
      ymax = +Inf
    ),
    fill = "lightblue",
    alpha = 0.5,
    color = NA
  )+
   geom_line(data = ocOut.comparison, aes(x = w, y = sum_pop, col = id), size = 1)+
  labs(x = "weeks (10 year)", 
       y = "population size", 
       col = "birth pattern", 
       title = "Comparison of seasonal vs non-seasonal (constant) birth pattern")



###########
## IMMUNITY 
##########


ggplot() +
  geom_rect(
   data = peakrect,
    aes(
      xmin = startpeak,
      xmax = endpeak,
      ymin = -Inf,
      ymax = +Inf
    ),
    fill = "lightblue",
    alpha = 0.5,
    color = NA
  )+
   geom_line(data = ocOut.comparison, aes(x = w, y = prop_immune, col = id), size = 1)+
  labs(x = "weeks (10 year)", 
       y = "population size", 
       col = "birth pattern", 
       title = "Immunity rates in Pastoral Goats with seasonal and non-seasonal (constant) births")+
  coord_cartesian(xlim=c(450,800))

```
# Review age-sex structure between seasonal and non-seasonal
```{r ocAgeSexCOmparison}


agesex.comparison <- bind_rows(ocOut.constant %>% select(w, sum_pop, starts_with("pf"), starts_with("pm")) %>% mutate(id = "constant"),
                   ocOut.seasonal %>% select(w, sum_pop, starts_with("pf"), starts_with("pm")) %>% mutate(id = "seasonal"))


agesex.long <- agesex.comparison %>%
  gather(key = "age_group", value = "prop", -c(w,id)) %>%
  mutate(age_group = factor(age_group, levels = c("pfAdu", "pfSub","pfKid","pmAdu","pmSub","pmKid","pF", "sum_pop")))


ggplot(agesex.long %>% filter(!age_group == "sum_pop"), 
       aes(x=w,y=prop), group = id)+
  geom_line(aes(col = id))+
  facet_wrap(~age_group, ncol = 3)


ggplot()+
  geom_rect(
   data = peakrect,
    aes(
      xmin = startpeak,
      xmax = endpeak,
      ymin = -Inf,
      ymax = +Inf
    ),
    fill = "lightblue",
    alpha = 0.5,
    color = NA
  )+
  geom_line(data = agesex.long %>% filter(!age_group %in% c("sum_pop", "pF") ),
            aes(x=w,y=prop,col = id, group = id))+
  facet_wrap(~age_group, scales = "free", ncol = 2)+
  theme_bw()

```
# Simulate full immunity dynamics following vaccination for all OC profiles with seasonal and non-seasonal reproduction

```{r seasonalDynLoop}


###################
## MODEL OUTPUT ##
###################
seasonal <- T
## Model Output
output <- "dynamics" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

# validOut = list to store outputs
GSAoutput <- c(); 
ocOut.seasonal <- list()


#####################
## DATA SELECTION ##
#####################

dataset <- datasets

if (dataset == "lesnoff.ft") {
  rates <- "wkly"
} else{
  rates <- "yrly"
}

fixdata <- dataset # set dataset for state_vars
vardata <- dataset
  
if(lhs){
  source("scripts/applied/applied_lhs.R") # output var_input_df contains all parameter combinations for uncertain demographics.
}

profOrder <- var_demo_data_full %>% select(prof) %>% pull()
var_input_backup <- var_demo_data_full %>% select(-prof)

#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")

ocOut.seasonal <- foreach (i = 1:nrow(var_input_backup),
                           .packages = c("dplyr", "tibble")) %dopar% {
                             print(i)
                             
                             var_input_full <- unlist(var_input_backup[i,])
                             
                             App_func(
                               imm_decay_corrected,
                               var_input_full,
                               fix_age_data_full,
                               f_list,
                               # initial state of female population
                               m_list,
                               # initial state of male population
                               TimeStop_dynamics,
                               # 1 year, weekly timestep for demographic component
                               TimeStop_transmission,
                               # 1 day, hourly timestep for transission component
                               output,
                               # model output: tracker or summary stats
                               summary_df,
                               #
                               clean_environment,
                               Vstart,
                               Vprog,
                               fixdata,
                               vardata,
                               birthpeak_w,
                               seasonal
                             )
                           }

```


```{r seasonalDynAnalysis}

# ocOut.dynamics
immDynamics <- lapply(ocOut.seasonal, select, prop_immune) %>%
  bind_cols() %>%
  t() %>%
  as.data.frame()

colnames(immDynamics) <- 1:ncol(immDynamics)
rownames(immDynamics) <- 1:nrow(immDynamics)

immDynamics.clean <- immDynamics %>%
  select((t2):ncol(immDynamics)) %>%
  mutate(prof = profOrder)

immDynamics.long <- immDynamics.clean %>%
  gather(key = "weeks", value = "prop_immune", -prof) %>%
  mutate(weeks = as.numeric(weeks))

# Calculate mean and confidence interval
summary_data <- immDynamics.long %>%
  group_by(prof,weeks) %>%
  summarise(
    mean_value = mean(prop_immune),
    lower_ci = quantile(prop_immune, 0.025),
    upper_ci = quantile(prop_immune, 0.975)
  )

plot_immVar <- ggplot(summary_data, aes(x = weeks, y = mean_value, group = prof)) +
  geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci, fill = prof), alpha = 0.5) +
  geom_line(aes(col = prof)) +
  geom_hline(yintercept = 0.7, linetype = "dashed")+
  # geom_vline(xintercept = Vprog$Vweek, col = "red")+
  facet_wrap(~prof, nrow = 2)+
  labs(x="Time (weeks)", y = "Proportion Immune", col = "Profile")+
  coord_cartesian(xlim = c(500,750))+
  scale_colour_manual(values = custom_palette)+
  scale_fill_manual(values = custom_palette)
plot_immVar

# filename_immVar <- "ImmDyn100_OCvalid.png"
# ggsave(paste0("plots/applied/",filename_immVar), plot = plot_immVar, width = 20, height = 10, units = "cm")

```


```{r ocConstantDynLoop}

seasonal <- F                        
ocOut.constant <- list()
#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")

ocOut.constant <- foreach (i = 1:nrow(var_input_backup),
                           .packages = c("dplyr", "tibble")) %dopar% {
                             print(i)
                             
                             var_input_full <- unlist(var_input_backup[i,])
                             
                             App_func(
                               imm_decay_corrected,
                               var_input_full,
                               fix_age_data_full,
                               f_list,
                               # initial state of female population
                               m_list,
                               # initial state of male population
                               TimeStop_dynamics,
                               # 1 year, weekly timestep for demographic component
                               TimeStop_transmission,
                               # 1 day, hourly timestep for transission component
                               output,
                               # model output: tracker or summary stats
                               summary_df,
                               #
                               clean_environment,
                               Vstart,
                               Vprog,
                               fixdata,
                               vardata,
                               birthpeak_w,
                               seasonal
                             )
                           }
stopCluster(cl)

```
# PLot immunity dyanmics post vaccination after 100% vacciantion coverage for seasonal and non-seasonal births in OC profiles
```{r constantDynAnalysis}

# ocOut.dynamics
immDynamics.constant <- lapply(ocOut.constant, select, prop_immune) %>%
  bind_cols() %>%
  t() %>%
  as.data.frame()

colnames(immDynamics.constant) <- 1:ncol(immDynamics.constant)
rownames(immDynamics.constant) <- 1:nrow(immDynamics.constant)

immDynamics.const.clean <- immDynamics.constant %>%
  select((t2):ncol(immDynamics.constant)) %>%
  mutate(prof = profOrder)

immDynamics.const.long <- immDynamics.const.clean %>%
  gather(key = "weeks", value = "prop_immune", -prof) %>%
  mutate(weeks = as.numeric(weeks))

# Calculate mean and confidence interval
summary_data.const <- immDynamics.const.long %>%
  group_by(prof,weeks) %>%
  summarise(
    mean_value = mean(prop_immune),
    lower_ci = quantile(prop_immune, 0.025),
    upper_ci = quantile(prop_immune, 0.975)
  )


summary_combined <- bind_rows(
  summary_data %>% mutate(births = "seasonal"),
  summary_data.const %>% mutate(births = "constant")
)

plot_immComp <- ggplot(summary_combined, aes(x = weeks, y = mean_value, group = births)) +
  geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci, fill = births), alpha = 0.5) +
  geom_line(aes(col = births)) +
  geom_hline(yintercept = 0.7, linetype = "dashed")+
  facet_wrap(~prof, nrow = 2)+
  labs(x="Time (weeks)", y = "Proportion Immune", col = "Profile")+
  coord_cartesian(xlim = c(500,750))

plot_immComp

# filename_immVar <- "ImmDyn100_OCvalid.png"
# ggsave(paste0("plots/applied/",filename_immVar), plot = plot_immVar, width = 20, height = 10, units = "cm")

# filename_immVar3m <- "ImmDynCompV3m_OCvalid.png"
# ggsave(paste0("plots/applied/",filename_immVar3m), plot = plot_immComp, width = 20, height = 10, units = "cm")
```

# Calculate summary statistics for post-vacciantion immunity with different pV levels, for seasonal and non-seasonal births, in all OC profiles

```{r seasonalVacSummary}


## Model Output
output <- "summary_all"
summary_df <- output_func(TimeStop_dynamics, output) 
ocOut.seasonalSumm <- c()
summ_i <- c()

# Seasonality 
seasonal <- T
BMonths <- c(3,6,9,12) # Birth peak months of the year (vacc is at month 1)


#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")

for(m in 1:length(BMonths)){
  
##################################
## BIRTH PEAKS  ##
##################################
birthpeak_w <- c()
peakmnth <- BMonths[m]  # Month of peak
peakstart <- wkmnthids %>% filter(mnth == peakmnth) %>% pull()
pkwk1 <- seq(from=peakstart, by=1, length.out=4)
for(i in 1:time_yrs-1){
  seqjump <- i*52
  pkwki <- pkwk1+seqjump
  birthpeak_w <- c(birthpeak_w,pkwki)
}

summ_i <- foreach (i = 1:nrow(var_input_backup),
                           .packages = c("dplyr", "tibble"),
                           .combine = "rbind") %dopar% {
                             print(i)
                             
                             var_input_full <- unlist(var_input_backup[i,])
                             
                             App_func(
                               imm_decay_corrected,
                               var_input_full,
                               fix_age_data_full,
                               f_list,
                               # initial state of female population
                               m_list,
                               # initial state of male population
                               TimeStop_dynamics,
                               # 1 year, weekly timestep for demographic component
                               TimeStop_transmission,
                               # 1 day, hourly timestep for transission component
                               output,
                               # model output: tracker or summary stats
                               summary_df,
                               #
                               clean_environment,
                               Vstart,
                               Vprog,
                               fixdata,
                               vardata,
                               birthpeak_w,
                               seasonal
                             )
                           }

ocOut.seasonalSumm <- bind_rows(ocOut.seasonalSumm,
                                summ_i %>% mutate("peakmnth" = peakmnth,
                                                  prof = profOrder, 
                                                  seasonal = seasonal) )
}

## add on non-seasonal results: 
seasonal <- F

summ_i <- foreach (i = 1:nrow(var_input_backup),
                           .packages = c("dplyr", "tibble"),
                           .combine = "rbind") %dopar% {
                             print(i)
                             
                             var_input_full <- unlist(var_input_backup[i,])
                             
                             App_func(
                               imm_decay_corrected,
                               var_input_full,
                               fix_age_data_full,
                               f_list,
                               # initial state of female population
                               m_list,
                               # initial state of male population
                               TimeStop_dynamics,
                               # 1 year, weekly timestep for demographic component
                               TimeStop_transmission,
                               # 1 day, hourly timestep for transission component
                               output,
                               # model output: tracker or summary stats
                               summary_df,
                               #
                               clean_environment,
                               Vstart,
                               Vprog,
                               fixdata,
                               vardata,
                               birthpeak_w,
                               seasonal
                             )
                           }

ocOut.summary <- bind_rows(ocOut.seasonalSumm %>% mutate(peakmnth = as.character(peakmnth)), 
                           summ_i %>% mutate(peakmnth = "none",
                                             prof = profOrder,
                                             seasonal = seasonal))

```


```{r ocOut.seasonalSumm}

ocOut.summdf <- ocOut.summary %>%
  mutate(prof_group = ifelse(grepl("*shp*", prof), "shp", "goat"),
    prof = factor(
      prof,
      levels = c("oc.goat.aridP","oc.goat.semiaridP","oc.goat.semiaridM","oc.goat.subhumidM","oc.goat.humidM",
                 "oc.shp.aridP","oc.shp.semiaridP","oc.shp.semiaridM","oc.shp.subhumidM", "oc.shp.humidM")), 
    peakmnth = factor(peakmnth, levels = c("3","6","9","12","none"))
  )

validImm <- ocOut.summdf %>%
  select(tenyr_growth, starts_with("imm"), peakmnth, prof, prof_group) %>%
  gather(key = "stat", value = "value", -c(prof,prof_group, peakmnth)) %>%
  mutate(stat = factor(stat, levels = c("imm_V0", "imm_6m", "imm_12m", "imm70_w", "tenyr_growth" )))

plot_immSh <- ggplot(validImm %>% filter(stat %in% c("imm_V0", "imm_6m", "imm_12m"), prof_group == "shp"), 
       aes(x = peakmnth, y = value))+ #, col = peakmnth
    geom_boxplot(alpha = 0.5, aes(fill = stat)) +
    geom_hline(yintercept = 0.7, linetype = "dashed")+
    facet_grid(prof~stat)+
    theme_bw()+
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
          legend.position = "none")+
  scale_fill_brewer(palette = "Dark2")
plot_immSh

plot_immGt <- ggplot(validImm %>% filter(stat %in% c("imm_V0", "imm_6m", "imm_12m"), prof_group == "goat"), 
       aes(x = peakmnth, y = value))+ #, col = peakmnth
    geom_boxplot(alpha = 0.5, aes(fill = stat)) +
    geom_hline(yintercept = 0.7, linetype = "dashed")+
    facet_grid(prof~stat)+
    theme_bw()+
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
          legend.position = "none")+
  scale_fill_brewer(palette = "Dark2")
plot_immGt

plot_imm70Sh <- ggplot(validImm %>% filter(stat %in% c("imm70_w"),prof_group == "shp"), 
            aes(x = peakmnth, y = value))+ #, col = peakmnth
  geom_boxplot(alpha = 0.5, fill = "grey") +
 facet_grid(prof~stat, scales = "free")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "none")
plot_imm70Sh

plot_tenyrSh <- ggplot(validImm %>% filter(stat %in% c("tenyr_growth"),prof_group == "shp"), 
            aes(x = peakmnth, y = value))+ # , col = peakmnth
  geom_boxplot(alpha = 0.5, fill = "grey") +
  facet_grid(prof~stat, scales = "free")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "none")
plot_tenyrSh



plot_immSh
plot_immGt
```