---
title: "oc_validation"
author: "Beth Savagar"
date: "2023-11-13"
output: html_document
---

# APPLIED EXAMPLES LHS - PRELIMINARY ANALYSIS 
- Analyse baseline demographics of applied examples with LHS of parameter space
- review population dynamics and age-sex structure, comparing against RSA demographic parameters
- check "validity" of output against initial conditions (RSA conditions): 15% growth, age-sex structure conditions

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library}
# libraries not accounted for in setup script
library(GGally)

```

```{r modSetup1}
############
## SETUP ##
############
local <- T
# local filepath: 
if(local){
  filepath <- ""
}else{
  # cluster filepath
  filepath <- "/storage/users/bsavagar/"
}

## Libraries
source(paste0(filepath,"scripts/setup.R")) 

## Functions:
source(paste0(filepath, "functions/Appliedfunc.R")) # wrapper function
source(paste0(filepath, "functions/demos_summary.R")) # summary stats for output
source(paste0(filepath, "functions/dynmod-vac.R")) # flock dynamics model function
source(paste0(filepath, "functions/output.R")) # what to include in output df
source(paste0(filepath, "functions/GSA_outputs.R")) # summary stats accounting for vac

```

## Demographic Parameters Check:

```{r ranges}
# how to valid parameters fit in the RSA GSA range

## Load parameters
datafile <- "-OC_check"
demographics <- read_csv(paste0("data/Applied_parameters/demographics",datafile,".csv"), col_names=T) 

checkRanges <- demographics %>%
  gather(key = "datasource", value = "value",-parameter) %>%
  mutate(
    datasource = gsub("\\.min|\\.max", "", datasource))

RSAonly <- checkRanges %>% 
  filter(datasource == "RSA") %>%
  mutate(datasource = "RSA.goat")

checkRanges <- checkRanges %>%
  rbind(RSAonly) %>%
  mutate(datasource = ifelse(datasource == "RSA", "RSA.shp", as.character(datasource)),
         data_group = ifelse(grepl("*shp*", datasource), "shp", "goat")) %>% 
  mutate(
    datasource = factor(
      datasource,
      levels = c(
        "oc.goat.aridP",
        "oc.goat.semiaridP",
        "oc.goat.semiaridM",
        "oc.goat.subhumidM",
        "oc.goat.humidM",
        "oc.shp.aridP",
        "oc.shp.semiaridP",
        "oc.shp.semiaridM",
        "oc.shp.subhumidM",
        "oc.shp.humidM",
        "RSA.shp",
        "RSA.goat"
      )
    )
  )


# Define the Dark2 palette with additional colors
custom_palette <- c(
  brewer.pal(8, "Dark2"),
  "#FFA07A",  # LightSalmon
  "#20B2AA",  # LightSeaGreen
  "#9370DB",  # MediumPurple
  "#32CD32",  # LimeGreen
  "#FFD700",  # Gold
  "#8A2BE2",  # BlueViolet
  "#FF4500",  # OrangeRed
  "#00CED1",  # DarkTurquoise
  "#000000"   # Black
)

myPal <- custom_palette[1:12]
myPal[11] <- "#000000"
myPal[12] <- "#000001"

p1<- ggplot(checkRanges %>% filter(parameter %in% c("adu_f_max_yrs", "adu_m_max_yrs","min_age_offtake","min_age_repro")), aes(x=parameter, y=value, col = datasource))+
  geom_point(position=position_dodge(width=0.2))+
  geom_line(size = 1, position=position_dodge(width=0.2))+
  labs(x = "Parameter")+
  facet_wrap(~data_group, scales = "free")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
       
        text = element_text(size=16))+
  scale_colour_manual(values = myPal)

p2 <- ggplot(checkRanges %>% filter(!parameter %in% c("adu_f_max_yrs", "adu_m_max_yrs","min_age_offtake","min_age_repro", "ppr_mortality_y", "ppr_mortality_a")), 
       aes(x=parameter, y=value, col = datasource))+
  geom_point(position=position_dodge(width=0.2))+
  geom_line(size = 1, position=position_dodge(width=0.2))+
  labs(x = "Parameter")+
  facet_wrap(~data_group, scales = "free")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
         legend.position = "none",
        text = element_text(size=16))+
  scale_colour_manual(values = myPal)

ggarrange(p1,p2, nrow = 2)


```


## 1. Verify Flock Dynamics
- For each profile run a sample of 50 parameter sets with full population dynamics simulated
- Plot the flock growth over time and the age-sex structure over time for preliminary analysis of model-profile behaviour

```{r selectData}
# 9/11/23: Run model with LHS of oc parameter space. Analyse results against original valid population conditions and against oc population growth reports. 

applied_example <- F

## Load parameters
datafile <- "-oc_check"
source(paste0(filepath, "scripts/applied/applied_load_data2.R")) 

## Datasets
datasets <- fix_age_data_full %>% select(-c(parameter, RSA)) %>% colnames()
```

```{r modSetup2}

######################
## MODEL SETUP ##
######################

## Simulation:
TimeStop_dynamics <- 20*52 # 2 years only interested in rates for 1 y
TimeStop_transmission <- 24 # 1 day, hourly timestep for transmission component
min_pop <- 1 # set minimum size of population, if pop drops below then set to 0

#######################
## Vaccination Setup ##
#######################
# see applied_vaccination
pV <- 1
source("scripts/applied/applied_vaccination.R")
Vstart <- Vprog %>% filter(Vround==1) %>% pull(Vweek)

##################
## RUN MODEL ##
##################

turnover <- F; 
dynamics <- T; 
transmission <- F; 
clean_environment <- T

# timepoints for population growth
t2 <- TimeStop_dynamics/2 # 5 year pop growth
t1 <- TimeStop_dynamics


##################################
## LHS SETUP  ##
##################################

lhs <- T
lhs_n <- 1e3 # number of sets (parameter combinations)
pairs_plot <- F
SA <- TRUE

```


```{r loopDynamics}

###################
## MODEL OUTPUT ##
###################

## Model Output
output <- "dynamics" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

# validOut = list to store outputs
GSAoutput <- c(); 
ocOut.dynamics <- list()

#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")


#####################
## LOOP ##
#####################

for(d in 1:length(datasets)){
  dataset <- datasets[d]
  data_filename <- gsub("\\.","",dataset)

  ##################################
  ## LHS DEMOGRAPHIC PARS ##
  ##################################
  
  data_filename <- gsub("\\.", "", dataset)
  
  if (dataset == "lesnoff.ft") {
    rates <- "wkly"
  } else{
    rates <- "yrly"
  }
  
  # set seed
  set.seed(1) # so that results are consistent
  
  pars_min <- paste0(dataset, ".min") # minimum val
  pars_max <-  paste0(dataset, ".max") # maximum val
  fixdata <- dataset # set dataset for state_vars
  vardata <- dataset
  
  source("scripts/applied/applied_lhs.R") # output var_input_df contains all parameter combinations for uncertain demographics.
  
  
  # Format demographic parameter sets:
  var_input_backup <- var_input_df %>% as.data.frame() %>% slice_sample(n = 10)
  
  ################
  ## SIMULATION ##
  ################
  Out.dynamics <- foreach (i = 1:nrow(var_input_backup),
                                .packages = c("dplyr", "tibble")) %dopar% {
                                  print(i)
                                  
                                  var_input_full <- unlist(var_input_backup[i, ])
                                  
                                  App_func(
                                    imm_decay_corrected,
                                    var_input_full,
                                    fix_age_data_full,
                                    f_list,# initial state of female population
                                    m_list, # initial state of male population
                                    TimeStop_dynamics,# 1 year, weekly timestep for demographic component
                                    TimeStop_transmission, # 1 day, hourly timestep for transission component
                                    output,# model output: tracker or summary stats
                                    summary_df, #
                                    clean_environment,
                                    Vstart,
                                    Vprog,
                                    fixdata,
                                    vardata
                                  )
                                }
  
  ocOut.dynamics[[d]] <- Out.dynamics
}

stopCluster(cl)

```


```{r analysisDynamics}

# ocOut.dynamics

# Transform Out (list) into a df of dynamics with each set identified:
dynamicsList <- lapply(ocOut.dynamics, function(x){
 do.call(rbind,x) %>% mutate(set = rep(1:10, each = TimeStop_dynamics))
  }) 
  
Out_dynamics <- dynamicsList %>%
  do.call(rbind, .) %>%
  mutate(prof = rep(datasets, each = 10400))


# Population Growth plot:
growth_dynplot <- ggplot(Out_dynamics, 
       aes(x = w, y = sum_pop, group = set)) + 
  labs(x="weeks", 
       y = "Population Size",
       title = "Population growth over 20 years, oc, (LHS Parameter Sets)")+
  geom_line()+
  facet_wrap(~prof)+
  theme_bw()

fadeout <- Out_dynamics %>% filter(sum_pop==0) %>% distinct(set) %>% pull()
fadeout_dynplot <- ggplot(Out_dynamics %>% filter(set %in% fadeout), 
       aes(x = w, y = sum_pop, group = set)) + 
  labs(x="weeks", 
       y = "Population Size",
       title = "Population growth over 20 years, oc, (LHS Parameter Sets)")+
  geom_line()+
    facet_wrap(~prof)+
  theme_bw()

# AgeSex Dynamics df: 
Out_agesex <- Out_dynamics %>% 
  select(c("w", "set", "prof", starts_with("pf"), starts_with("pm"))) %>% 
  gather(key = "par", value = value, -c(w,set,prof)) %>%
  mutate(par = factor(par, levels = c("pfAdu", "pfSub", "pfKid", 
                                         "pmAdu","pmSub","pmKid",
                                         "pF"))) %>%
  mutate(prof_group = ifelse(grepl("*shp*", prof), "shp", "goat"))

# Age-Sex Plot:
agesex_dynplotG <- ggplot(Out_agesex %>% filter(prof_group=="goat"), 
       aes(x = w, y = value, group = set, col = prof)) + 
  geom_line()+
  facet_grid(par~prof)+
  labs(x="Weeks", 
       y = "Proportion",
       title = "Age-Sex dynamics, oc, (LHS Parameter Sets)")+
  theme_bw()+
  scale_colour_manual(values = myPal)

agesex_dynplotSh <-  ggplot(Out_agesex %>% filter(prof_group=="shp"), 
       aes(x = w, y = value, group = set, col = par)) + 
  geom_line()+
  facet_grid(par~prof)+
  labs(x="Weeks", 
       y = "Proportion",
       title = "Age-Sex dynamics, oc, (LHS Parameter Sets)")+
  theme_bw()+
  scale_colour_manual(values = myPal)

growth_dynplot
# fadeout_dynplot
agesex_dynplotG
agesex_dynplotSh

```


```{r loopSummary}

## Model Output
output <- "summary_all" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

# validOut = list to store outputs
GSAoutput <- c(); 
ocOut.sum <- list()

#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")


#####################
## LOOP ##
#####################

for(d in 1:length(datasets)){
  dataset <- datasets[d]
  data_filename <- gsub("\\.","",dataset)
  
  ##################################
  ## LHS DEMOGRAPHIC PARS ##
  ##################################
  
  data_filename <- gsub("\\.", "", dataset)
  
  if (dataset == "lesnoff.ft") {
    rates <- "wkly"
  } else{
    rates <- "yrly"
  }
  
  # set seed
  set.seed(1) # so that results are consistent
  
  pars_min <- paste0(dataset, ".min") # minimum val
  pars_max <-  paste0(dataset, ".max") # maximum val
  fixdata <- dataset # set dataset for state_vars
  vardata <- dataset
  
  source("scripts/applied/applied_lhs.R") # output var_input_df contains all parameter combinations for uncertain demographics.
  
  
  # Format demographic parameter sets:
  var_input_backup <- var_input_df %>% as.data.frame()  %>% slice_sample(n = 100)
  
  ################
  ## SIMULATION ##
  ################
  Out.summary <- foreach (i = 1:nrow(var_input_backup),
                                .packages = c("dplyr", "tibble"),
                          .combine = "rbind") %dopar% {
                                  print(i)
                                  
                                  var_input_full <- unlist(var_input_backup[i, ])
                                  
                                  App_func(
                                    imm_decay_corrected,
                                    var_input_full,
                                    fix_age_data_full,
                                    f_list,# initial state of female population
                                    m_list, # initial state of male population
                                    TimeStop_dynamics,# 1 year, weekly timestep for demographic component
                                    TimeStop_transmission, # 1 day, hourly timestep for transission component
                                    output,# model output: tracker or summary stats
                                    summary_df, #
                                    clean_environment,
                                    Vstart,
                                    Vprog,
                                    fixdata,
                                    vardata
                                  )
                                }
  
  ocOut.sum[[d]] <- Out.summary
}

stopCluster(cl)

```


```{r analysisSummary}

################################
## POP & AGE-SEX SUMMARY ##
################################

# ocOut.summary is a dataframe of summary data for each parameter set 

## Plot population growth stats: 
# - Total Growth (20y), 
# - tenyr Growth (10y), 
# - Finyr Growth (1y)

summaryList <- ocOut.sum
ocOut.summary <- summaryList %>%
  do.call(rbind, .) %>%
  mutate(prof = rep(datasets, each = 100), 
         set = rep(1:100, length(datasets))) %>% 
  replace(is.na(.), 0) %>%
  mutate(prof_group = ifelse(grepl("*shp*", prof), "shp", "goat"),
    prof = factor(
      prof,
      levels = c(
        "oc.goat.aridP",
        "oc.goat.semiaridP",
        "oc.goat.semiaridM",
        "oc.goat.subhumidM",
        "oc.goat.humidM",
        "oc.shp.aridP",
        "oc.shp.semiaridP",
        "oc.shp.semiaridM",
        "oc.shp.subhumidM",
        "oc.shp.humidM"
      )
    )
  )

# df of population growth stats:
popgrowth <- ocOut.summary %>% 
  select(prof, prof_group, ends_with("growth")) %>% 
  gather(key = "par", value = "prop", -c(prof,prof_group)) %>% 
  mutate(par = factor(par, levels = c("pop_growth",
                                      "tenyr_growth", 
                                      "twoyr_growth",
                                      "finyr_growth")))

growth_boxplot <- ggplot(popgrowth, aes(x=prof, y = prop, col = prof))+
  geom_boxplot(alpha = 0.5)+
  facet_wrap(~par, scales = "free", nrow = 1)+
  labs(x = "Growth Stat", 
       y = "Pop Growth",
       title = "Growth statistics for oc data, LHS parameter sets")+
  theme_bw()+
  scale_colour_manual(values = myPal)

growth_histGoat <- ggplot(popgrowth %>% filter(prof_group == "goat"), aes(prop))+
  geom_histogram()+
  facet_grid(prof~par, scales = "free")+
  labs(x = "Pop Growth", 
       y = "Count")+
  theme_bw()

growth_histShp <- ggplot(popgrowth %>% filter(prof_group == "goat"), aes(prop))+
  geom_histogram()+
  facet_grid(prof~par, scales = "free")+
  labs(x = "Pop Growth", 
       y = "Count")+
  theme_bw()

growth_boxplot
growth_histGoat
growth_histShp
##
##

## Analyse age-sex dynamics:

# - Age-Sex plots
agesex <- ocOut.summary %>% 
  select(prof, prof_group, starts_with("pf"), starts_with("pm")) %>% 
  gather(key = "par", value = "prop", -c(prof,prof_group))

agesex_boxplot <- ggplot(agesex, aes(x=par, y = prop))+
  geom_boxplot(fill = "grey", 
               alpha = 0.5)+
  labs(x="Age-Sex Group", 
       y = "Proportion",
       title = "Stable Age-Sex structure, oc, (LHS parameter sets)")+
  theme_bw()+
  facet_wrap(~prof, ncol = 5)

agesex_boxplot2 <- ggplot(agesex, aes(x=prof, y = prop))+
  geom_boxplot(fill = "grey", 
               alpha = 0.5)+
  labs(x="Age-Sex Group", 
       y = "Proportion",
       title = "Stable Age-Sex structure, oc, (LHS parameter sets)")+
  theme_bw()+
  facet_wrap(~par, ncol = 4)
  
agesex_boxplot


```


```{r outValid}
#------------------------------------------------------------------------------
## VALID RESULTS ##

##################################
## Valid Age-Sex Conditions ##
##################################

## Min and max proportions for each sex-age group (see age-sex SS)
pfKid.min <- 0.05; pfKid.max <- 0.19
pfSub.min <- 0.06; pfSub.max <- 0.19
pfAdu.min <- 0.21; pfAdu.max <- 0.62

pmKid.min <- 0.05; pmKid.max <- 0.16
pmSub.min <- 0.04; pmSub.max <- 0.15
pmAdu.min <- 0.01; pmAdu.max <- 0.15
  

#########################################################
# Retain behavioral parameter sets
#########################################################

# Edit Out to contain identifier variables for pop growth (5%,15%) and pop growth with age-sex structure 
ocOut.growth <- ocOut.summary %>%
  mutate(tenyr_growth = replace_na(tenyr_growth, 0),
         # add variables to identify parameter sets with growth between 5% and 15%
         tenyr_15 = ifelse(tenyr_growth>=0.85 & tenyr_growth <=1.15, 1, 0),
         tenyr_05 = ifelse(tenyr_growth>=0.95 & tenyr_growth <=1.05, 1, 0)) %>%
  
  # add variables to identify parameter sets with growth between 5% and 15% AND age-sex conditions
  mutate(
    tenyr_15age = ifelse(
      tenyr_15 == 1 &
        pfKid >= pfKid.min & pfKid <= pfKid.max &
        pfSub >= pfSub.min & pfSub <= pfSub.max &
        pfAdu >= pfAdu.min & pfAdu <= pfAdu.max &
        
        pmKid >= pmKid.min & pmKid <= pmKid.max &
        pmSub >= pmSub.min & pmSub <= pmSub.max &
        pmAdu >= pmAdu.min & pmAdu <= pmAdu.max,1,0),
    
    tenyr_05age = ifelse(
      tenyr_05 == 1 &
        pfKid >= pfKid.min & pfKid <= pfKid.max &
        pfSub >= pfSub.min & pfSub <= pfSub.max &
        pfAdu >= pfAdu.min & pfAdu <= pfAdu.max &
        
        pmKid >= pmKid.min & pmKid <= pmKid.max &
        pmSub >= pmSub.min & pmSub <= pmSub.max &
        pmAdu >= pmAdu.min & pmAdu <= pmAdu.max,1,0)
  )

ocOut.growth %>% group_by(prof,tenyr_15age) %>% count() %>% kable()

# Growth easily within RSA conditions


# ##################
# ## Valid Output ##
# ##################

ocOut.valid <- ocOut.growth %>%
  filter(tenyr_15age == 1 |
           tenyr_05age == 1)

## Refine parameter dataframe:
ocPars.valid <- var_input_backup %>%
  mutate(set = 1:nrow(var_input_backup)) %>%
  left_join(ocOut.valid %>%
              select(tenyr_growth,
                     tenyr_15,
                     tenyr_05,
                     tenyr_15age,
                     tenyr_05age,
                     set), by = c("set")) %>%
  filter(tenyr_15age == 1 |
           tenyr_05age == 1)  %>%
  select(-c(tenyr_15,
            tenyr_05,
            set))


pairs(ocPars.valid %>% select(-c(tenyr_growth,tenyr_05age,tenyr_15age)))

```