---
title: "validvac_seasonalFixed_Appendices"
author: "Beth Savagar"
date: "2023-12-11"
output: html_document
---

# Script for immunity analysis of flock profiles with seasonal reproduction:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library}
# libraries not accounted for in setup script
library(GGally)
plotsave <- F
custom_theme <- theme_bw() + 
  theme(text = element_text(family = "Times New Roman", size = 10),
        panel.grid.minor = element_blank())
theme_set(custom_theme)
# custom_palette <- c("#004D40", "#00695C", "#00796B", "#00897B", "#009688", "#4A148C", "#6A1B9A", "#7B1FA2", "#8E24AA", "#9C27B0")

```

```{r modSetup1}
############
## SETUP ##
############
local <- T
# local filepath: 
if(local){
  filepath <- ""
}else{
  # cluster filepath
  filepath <- "/storage/users/bsavagar/"
}

## Libraries
source(paste0(filepath,"scripts/setup.R")) 

## Functions:
source(paste0(filepath, "functions/Appliedfunc_seasonalfixed.R")) # wrapper function
source(paste0(filepath, "functions/demos_summary.R")) # summary stats for output
source(paste0(filepath, "functions/dynmod-vac_seasonalfixed.R")) # flock dynamics model function
source(paste0(filepath, "functions/output.R")) # what to include in output df
source(paste0(filepath, "functions/GSA_outputs.R")) # summary stats accounting for vac

```


```{r selectData}
# 9/11/23: Run model with LHS of oc parameter space. Analyse results against original valid population conditions and against oc population growth reports. 

applied_example <- T

## Load parameters
datafile <- "-OC_validPars-seasonal"
fix_age_data_full <- read_csv(paste0("data/Applied_parameters/state_vars",datafile,".csv"),col_names=T)
var_demo_data_full <- read_csv(paste0("output/Applied/applied_outValidPars_OC_2023-12-11.csv"))
# load mean annual birth rate (calc from validVac non-seasonal.Rmd)
nBirths_df <- read_csv("output/Applied/stableAgeSex/Applied_nBirths_OC.csv")
imm_decay_corrected <- read_csv("data/imm_decay_bodjo_v2.csv") 

## Datasets
datasets <- fix_age_data_full %>% select(-parameter) %>% colnames()
#combine nBirths with other demogrpahics
var_demo_data_full <- var_demo_data_full %>%
  mutate(nBirths_yr = nBirths_df$mean)

```

```{r modSetup}

######################
## MODEL SETUP ##
######################

## Simulation:
TimeStop_dynamics <- 20*52 # 2 years only interested in rates for 1 y
TimeStop_transmission <- 24 # 1 day, hourly timestep for transmission component
min_pop <- 1 # set minimum size of population, if pop drops below then set to 0


##################
## RUN MODEL ##
##################

turnover <- F; 
dynamics <- T; 
transmission <- F; 
clean_environment <- T
seasonal <- T

# timepoints for population growth
t2 <- TimeStop_dynamics/2 # 5 year pop growth
t1 <- TimeStop_dynamics


##################################
## BIRTH PEAKS  ##
##################################

# id which week of the year each month starts on:
wkmnthids <- data.frame(
  mnth = 1:12,
  mnthwk = seq(1,53, by = 4.345) %>% round()
)

peakmnth <- 1  # Month of peak
peakstart <- wkmnthids %>% filter(mnth == peakmnth) %>% pull()
pkwk1 <- seq(from=peakstart, by=1, length.out=8)
birthpeak_w <- c()
time_yrs <- TimeStop_dynamics/52
for(i in 1:time_yrs-1){
  seqjump <- i*52
  pkwki <- pkwk1+seqjump
  birthpeak_w <- c(birthpeak_w,pkwki)
}

##################################
## LHS SETUP  ##
##################################

lhs <- F
lhs_n <- 0 # number of sets (parameter combinations)
pairs_plot <- F
SA <- F

```

Vaccination simulations:
- 4 rounds: year 1: >4m, year 2-4: 4m-12m
- coverages: 70,80,90,100
- schedules: V1 = 3m before birth peak, V2-V4 = 4m after birth peak
Appendices:
- Optimal vaccination schedule: 
    - y1 = ~6m before birth peak (high proportion of eligible animals & mat antibodies passed on to offspring)
    - y2 onwards = 3-4m after end of birth peak when all offspring have lost maternal immunity
    --> V1 (-6m), V2 = +10m after V1, V3 = +1y after V2, 

```{r vaccinationSchedule}

#######################
## Vaccination Setup ##
#######################
# see applied_vaccination
pVs <-c(0.7,0.8,0.9,1)
pV <- 1

## GSCE Vaccination: 
V_rounds <- 4 # number of campaigns (GSCE recommended)
V_breaks <- 52 # uneven

# 6 months before birth peak:
V1 = round(t2+(6*4.345),0)
V2 = round(V1 + 11*4.345) # 11m after first vaccination (6m following initial vaccination+3m following end of birth peak)
V3 = round(V2 + 52) # 12m after second round (when offspring become susceptible)
V4 = round(V3 + 52)

V_age_min <- round(4 *4.345,0) # 4 months (4.345 weeks per month)
# *** Update to 16m so no animal is missed ***
V_age_max <- round(12*4.345,0) # 12 months (4.345 weeks per month) for partial campaigns

Vprog <- data.frame(
  Vround = 1:V_rounds,
  Vtype = c("full","partial","partial","partial"),
  Vweek = c(V1,V2,V3,V4),
  Vmin = V_age_min,
  Vmax = c(NA, V_age_max, V_age_max, V_age_max),
  pV = rep(pV, V_rounds)
)

Vstart <- Vprog %>% filter(Vround==1) %>% pull(Vweek)

```


# Simulate full immunity dynamics following vaccination for all OC profiles with non-seasonal reproduction

```{r DynLoop}

###################
## MODEL OUTPUT ##
###################
seasonal <- T
## Model Output
output <- "dynamics" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

# validOut = list to store outputs
GSAoutput <- c(); 
ocOut.seasonal <- list()

#####################
## DATA SELECTION ##
#####################

dataset <- datasets

if (dataset == "lesnoff.ft") {
  rates <- "wkly"
} else{
  rates <- "yrly"
}

fixdata <- dataset # set dataset for state_vars
vardata <- dataset
  
# filter to profiles with non-seasonal reproduction
var_demo_data_profs <- var_demo_data_full %>%
  filter(prof %in% c("oc.goat.aridP",
                     "oc.goat.semiaridP",
                     "oc.shp.aridP",
                     "oc.shp.semiaridP"))

profOrder <- var_demo_data_profs %>% select(prof) %>% pull()
var_input_backup <- var_demo_data_profs %>% select(-prof)

```

```{r runMod}

#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")

A.seasonal <- c()
Adyn_i.clean <- c() # dataframe for expanded immunity dynamics


for(v in 1:length(pVs)){
  
  Vprog$pV <- rep(pVs[v], V_rounds)
    
  Vstart <- Vprog %>% filter(Vround==1) %>% pull(Vweek)
  
  A.seasonal <- foreach (i = 1:nrow(var_input_backup),
                           .packages = c("dplyr", "tibble")) %dopar% {
                             print(i)
                             
                             var_input_full <- unlist(var_input_backup[i,])
                             
                             App_func(
                               imm_decay_corrected,
                               var_input_full,
                               fix_age_data_full,
                               f_list,
                               # initial state of female population
                               m_list,
                               # initial state of male population
                               TimeStop_dynamics,
                               # 1 year, weekly timestep for demographic component
                               TimeStop_transmission,
                               # 1 day, hourly timestep for transission component
                               output,
                               # model output: tracker or summary stats
                               summary_df,
                               #
                               clean_environment,
                               Vstart,
                               Vprog,
                               fixdata,
                               vardata,
                               birthpeak_w,
                               seasonal
                             )
                           }
  
  Adyn_i <- lapply(A.seasonal , select, prop_immune) %>%
  bind_cols() %>%
  t() %>%
  as.data.frame()
  
  colnames(Adyn_i) <- 1:ncol(Adyn_i)
  rownames(Adyn_i) <- 1:nrow(Adyn_i)
  
  Adyn_i.clean <- Adyn_i.clean %>% 
    bind_rows(
      Adyn_i %>%
        select((t2):ncol(Adyn_i)) %>%
        mutate(prof = profOrder,
               pV = pVs[v])
    )
  }

stopCluster(cl)

```

```{r DynamicsAnalysis}

AimmDynamics.long <- Adyn_i.clean %>%
  gather(key = "weeks", value = "prop_immune", -c(prof, pV)) %>%
  mutate(weeks = as.numeric(weeks))

# Calculate mean and confidence interval
Asummary_data <- AimmDynamics.long %>%
  group_by(pV,prof,weeks) %>%
  summarise(
    mean_value = mean(prop_immune),
    lower_ci = quantile(prop_immune, 0.025),
    upper_ci = quantile(prop_immune, 0.975)
  )

plotA_immVar <- ggplot(Asummary_data, aes(x = weeks, y = mean_value, group = factor(pV))) +
  #geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci, fill = factor(pV)), alpha = 0.5) +
  geom_line(aes(col = factor(pV))) +
  geom_hline(yintercept = 0.7, linetype = "dashed")+
  facet_wrap(~prof)+ # facet_grid(pV~prof)+
  guides(fill = "none")+
  labs(x="Time (weeks)", y = "Proportion Immune", col = "pV")+
  coord_cartesian(xlim = c(500,750))

plotA_immVar


plot_immVarApp <-ggplot(Asummary_data, aes(x = weeks, y = mean_value, group = factor(pV))) +
  # geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci, fill = factor(pV)), alpha = 0.5) +
  geom_line(aes(col = factor(pV)), size = 0.7) +
  geom_hline(yintercept = 0.7, linetype = "dashed")+
  facet_grid(~prof)+
  guides(fill = "none")+
  labs(x="Time (years)", y = "Flock proportion immune", col = "pV")+
  coord_cartesian(xlim = c(520,755))+
  scale_x_continuous(breaks = seq(520, 755, by = 26), labels = seq(520, 755, by = 26) / 52)+
  scale_colour_brewer(palette = "RdYlBu")+
  scale_fill_brewer(palette = "RdYlBu")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

plot_immVarApp

# with Vweeks
plot_immVarApp2 <- ggplot(Asummary_data %>% filter(Vweeks >=0 & mean_value>0), # so x-axis starts at day 1 of vaccination
                      aes(x = Vweeks, y = mean_value, group = factor(pV))) +
  # show uncertainty for pV = 1 only
  geom_ribbon(data = summary_data %>% filter(pV == 1, Vweeks >=0 & mean_value>0), 
              aes(x = Vweeks, ymin = lower_ci, ymax = upper_ci), 
              fill = "#4575B4", alpha = 0.5) +
  geom_line(aes(col = factor(pV)), size = 0.7) +
  geom_hline(yintercept = 0.7, linetype = "dashed")+
  facet_grid(prof~Vstart, scales = "free_x")+
  guides(position = "top", fill = "none")+
  labs(x="Time post-vaccination (years)", y = "Flock proportion immune", col = "pV")+
  coord_cartesian(xlim = c(NA,220), ylim = c(0,1))+
  scale_x_continuous(breaks = seq(0, 220, by = 26), labels = seq(0, 220, by = 26) / 52)+
  scale_colour_brewer(palette = "RdYlBu")+
  scale_fill_brewer(palette = "RdYlBu")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "top")


# filename_immVar <- "OC_seasonalDyn.png"
# ggsave(paste0("plots/applied/",filename_immVar), plot = plot_immVar, width = 20, height = 10, units = "cm")

```

##############################
## VACCINATION 2Mo ##
##############################


```{r vaccinationSchedule}

#######################
## Vaccination Setup ##
#######################
# see applied_vaccination
pVs <-c(0.7,0.8,0.9,1)
pV <- 1

## GSCE Vaccination: 
V_rounds <- 4 # number of campaigns (GSCE recommended)
V_breaks <- 52 # uneven

# 6 months before birth peak:
V1 = round(t2+(6*4.345),0)
V2 = round(V1 + 47) # 6m following initial vaccination+ (8-week birth peak +) 13 weeks following end of birth peak (min age vaccination)
V3 = round(V2 + 52) # 12m after second round (when offspring become susceptible)
V4 = round(V3 + 52)

V_age_min <- round(3*4.345,0) # 4 months (4.345 weeks per month)
# *** Update to 16m so no animal is missed ***
V_age_max <- round(12*4.345,0) # 12 months (4.345 weeks per month) for partial campaigns

Vprog <- data.frame(
  Vround = 1:V_rounds,
  Vtype = c("full","partial","partial","partial"),
  Vweek = c(V1,V2,V3,V4),
  Vmin = V_age_min,
  Vmax = c(NA, V_age_max, V_age_max, V_age_max),
  pV = rep(pV, V_rounds)
)

Vstart <- Vprog %>% filter(Vround==1) %>% pull(Vweek)

```


```{r runMod}
output <- "dynamics" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 
#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")

A2.seasonal <- c()
A2dyn_i.clean <- c() # dataframe for expanded immunity dynamics


for(v in 1:length(pVs)){
  
  Vprog$pV <- rep(pVs[v], V_rounds)
    
  Vstart <- Vprog %>% filter(Vround==1) %>% pull(Vweek)
  
  A2.seasonal <- foreach (i = 1:nrow(var_input_backup),
                           .packages = c("dplyr", "tibble")) %dopar% {
                             print(i)
                             
                             var_input_full <- unlist(var_input_backup[i,])
                             
                             App_func(
                               imm_decay_corrected,
                               var_input_full,
                               fix_age_data_full,
                               f_list,
                               # initial state of female population
                               m_list,
                               # initial state of male population
                               TimeStop_dynamics,
                               # 1 year, weekly timestep for demographic component
                               TimeStop_transmission,
                               # 1 day, hourly timestep for transission component
                               output,
                               # model output: tracker or summary stats
                               summary_df,
                               #
                               clean_environment,
                               Vstart,
                               Vprog,
                               fixdata,
                               vardata,
                               birthpeak_w,
                               seasonal
                             )
                           }
  
  A2dyn_i <- lapply(A2.seasonal , select, prop_immune) %>%
  bind_cols() %>%
  t() %>%
  as.data.frame()
  
  colnames(A2dyn_i) <- 1:ncol(A2dyn_i)
  rownames(A2dyn_i) <- 1:nrow(A2dyn_i)
  
  A2dyn_i.clean <- A2dyn_i.clean %>% 
    bind_rows(
      A2dyn_i %>%
        select((t2):ncol(A2dyn_i)) %>%
        mutate(prof = profOrder,
               pV = pVs[v])
    )
  }

stopCluster(cl)

```

```{r A2dynamics}
# 
# A2immDynamics.long <- AimmDynamics.long %>%
#   mutate(Vmin = "17w") %>%
#   bind_rows(
#     A2dyn_i.clean %>%
#     gather(key = "weeks", value = "prop_immune", -c(prof, pV)) %>%
#     mutate(weeks = as.numeric(weeks), Vmin = "11w")
#   )

A2immDynamics.long <- A2dyn_i.clean %>%
    gather(key = "weeks", value = "prop_immune", -c(prof, pV)) %>%
    mutate(weeks = as.numeric(weeks), 
           Vweeks = weeks - V1,
           Vmin = "13w")
  
# Calculate mean and confidence interval
A2summary_data <- A2immDynamics.long %>%
  group_by(pV,prof,weeks,Vweeks,Vmin) %>%
  summarise(
    mean_value = mean(prop_immune),
    lower_ci = quantile(prop_immune, 0.025),
    upper_ci = quantile(prop_immune, 0.975)
  )

plot_immVarApp2 <-ggplot(A2summary_data, aes(x = weeks, y = mean_value, group = factor(pV))) +
  # geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci, fill = factor(pV)), alpha = 0.5) +
  geom_line(aes(col = factor(pV)), size = 0.7) +
  geom_hline(yintercept = 0.7, linetype = "dashed")+
  facet_grid(Vmin~prof)+
  guides(fill = "none")+
  labs(x="Time (years)", y = "Flock proportion immune", col = "pV")+
  coord_cartesian(xlim = c(520,755))+
  scale_x_continuous(breaks = seq(520, 755, by = 26), labels = seq(520, 755, by = 26) / 52)+
  scale_colour_brewer(palette = "RdYlBu")+
  scale_fill_brewer(palette = "RdYlBu")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

plot_immVarApp2

plot_immVarAppN2 <- ggplot(A2summary_data %>% filter(Vweeks >=0 & mean_value>0), # so x-axis starts at day 1 of vaccination
                      aes(x = Vweeks, y = mean_value, group = factor(pV))) +
  # show uncertainty for pV = 1 only
  geom_ribbon(data = A2summary_data %>% filter(pV == 1, Vweeks >=0 & mean_value>0), 
              aes(x = Vweeks, ymin = lower_ci, ymax = upper_ci), 
              fill = "#4575B4", alpha = 0.5) +
  geom_line(aes(col = factor(pV)), size = 0.7) +
  geom_hline(yintercept = 0.7, linetype = "dashed")+
  facet_grid(Vmin~prof, scales = "free_x")+
  guides(position = "top", fill = "none")+
  labs(x="Time post-vaccination (years)", y = "Flock proportion immune", col = "pV")+
  coord_cartesian(xlim = c(NA,220), ylim = c(0,1))+
  scale_x_continuous(breaks = seq(0, 220, by = 26), labels = seq(0, 220, by = 26) / 52)+
  scale_colour_brewer(palette = "RdYlBu")+
  scale_fill_brewer(palette = "RdYlBu")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "top")

if(plotsave){
  filename_immVarAppN2 <- "OC_seasonalDyn_App.png"
  ggsave(paste0("plots/applied/",filename_immVarAppN2), plot = plot_immVarAppN2, width = 20, height = 10, units = "cm")
}
```


######################
## Summary output ##
######################


```{r vaccinationSchedule1}

#######################
## Vaccination Setup ##
#######################
# see applied_vaccination
pVs <-c(0.7,0.8,0.9,1)
pV <- 1

## GSCE Vaccination: 
V_rounds <- 4 # number of campaigns (GSCE recommended)
V_breaks <- 52 # uneven

# 6 months before birth peak:
V1 = round(t2+(6*4.345),0)
V2 = round(V1 + 11*4.345) # 11m after first vaccination (4m following initial vaccination+4m following end of birth peak)
V3 = round(V2 + 52) # 12m after second round (when offspring become susceptible)
V4 = round(V3 + 52)

V_age_min <- round(4 *4.345,0) # 4 months (4.345 weeks per month)
# *** Update to 16m so no animal is missed ***
V_age_max <- round(12*4.345,0) # 12 months (4.345 weeks per month) for partial campaigns

Vprog <- data.frame(
  Vround = 1:V_rounds,
  Vtype = c("full","partial","partial","partial"),
  Vweek = c(V1,V2,V3,V4),
  Vmin = V_age_min,
  Vmax = c(NA, V_age_max, V_age_max, V_age_max),
  pV = rep(pV, V_rounds)
)

Vstart <- Vprog %>% filter(Vround==1) %>% pull(Vweek)

```

```{r runMod2}

seasonal <- T
## Model Output
output <- "summary_all" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

# validOut = list to store outputs
GSAoutput <- c(); 
A.seasonalSumm <- c()
#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")


for (v in 1:length(pVs)) {
  Vprog$pV <- rep(pVs[v], V_rounds)
  
  Vstart <- Vprog %>% filter(Vround == 1) %>% pull(Vweek)
  
  summ_i <- foreach (
    i = 1:nrow(var_input_backup),
    .packages = c("dplyr", "tibble"),
    .combine = "rbind"
  ) %dopar% {
    print(i)
    
    var_input_full <-
      unlist(var_input_backup[i, ])
    
    App_func(
      imm_decay_corrected,
      var_input_full,
      fix_age_data_full,
      f_list,
      # initial state of female population
      m_list,
      # initial state of male population
      TimeStop_dynamics,
      # 1 year, weekly timestep for demographic component
      TimeStop_transmission,
      # 1 day, hourly timestep for transission component
      output,
      # model output: tracker or summary stats
      summary_df,
      #
      clean_environment,
      Vstart,
      Vprog,
      fixdata,
      vardata,
      birthpeak_w,
      seasonal
    )
  }
  
  
  A.seasonalSumm <- bind_rows(A.seasonalSumm,
                              summ_i %>%
                                mutate(prof = profOrder,
                                       pV = pVs[v]))
}


stopCluster(cl)


#  Start from here if not wanting to run the model:
# filename_immDyn_seasonalSumm <- "immDyn_seasonalSumm.csv"
# write.csv(ocOut.seasonalSumm, file = paste0("output/Applied/", filename_immDyn_seasonalSumm))
```


```{r vaccinationSchedule1}

#######################
## Vaccination Setup ##
#######################
# see applied_vaccination
pVs <-c(0.7,0.8,0.9,1)
pV <- 1

## GSCE Vaccination: 
V_rounds <- 4 # number of campaigns (GSCE recommended)
V_breaks <- 52 # uneven

# 6 months before birth peak:
V1 = round(t2+(6*4.345),0)
V2 = round(V1 + 10*4.345) # 11m after first vaccination (3m following initial vaccination+4m following end of birth peak)
V3 = round(V2 + 52) # 12m after second round (when offspring become susceptible)
V4 = round(V3 + 52)

V_age_min <- round(3*4.345,0) # 4 months (4.345 weeks per month)
# *** Update to 16m so no animal is missed ***
V_age_max <- round(12*4.345,0) # 12 months (4.345 weeks per month) for partial campaigns

Vprog <- data.frame(
  Vround = 1:V_rounds,
  Vtype = c("full","partial","partial","partial"),
  Vweek = c(V1,V2,V3,V4),
  Vmin = V_age_min,
  Vmax = c(NA, V_age_max, V_age_max, V_age_max),
  pV = rep(pV, V_rounds)
)

Vstart <- Vprog %>% filter(Vround==1) %>% pull(Vweek)

```

```{r runMod2}

seasonal <- T
## Model Output
output <- "summary_all" # Output options: "summary" (stats with age-group prop), "summary_all" (stats with age-sex group prop), "dynamics" (pop metrics over time)
# create empty dataframe to store output
summary_df <- output_func(TimeStop_dynamics, output) 

# validOut = list to store outputs
GSAoutput <- c(); 
A2.seasonalSumm <- c()
#####################
## PARALLELISATION ##
#####################

print("start-parallel")

## Local parallelisation
if(local){
  cores=detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
}else{
  cores=detectCores()
  cl <- makeCluster(10)
  registerDoParallel(cl)
}
print("parallel-verified")
print("start-model")


for (v in 1:length(pVs)) {
  Vprog$pV <- rep(pVs[v], V_rounds)
  
  Vstart <- Vprog %>% filter(Vround == 1) %>% pull(Vweek)
  
  summ_i <- foreach (
    i = 1:nrow(var_input_backup),
    .packages = c("dplyr", "tibble"),
    .combine = "rbind"
  ) %dopar% {
    print(i)
    
    var_input_full <-
      unlist(var_input_backup[i, ])
    
    App_func(
      imm_decay_corrected,
      var_input_full,
      fix_age_data_full,
      f_list,
      # initial state of female population
      m_list,
      # initial state of male population
      TimeStop_dynamics,
      # 1 year, weekly timestep for demographic component
      TimeStop_transmission,
      # 1 day, hourly timestep for transission component
      output,
      # model output: tracker or summary stats
      summary_df,
      #
      clean_environment,
      Vstart,
      Vprog,
      fixdata,
      vardata,
      birthpeak_w,
      seasonal
    )
  }
  
  
  A2.seasonalSumm <- bind_rows(A2.seasonalSumm,
                              summ_i %>%
                                mutate(prof = profOrder,
                                       pV = pVs[v]))
}


stopCluster(cl)


#  Start from here if not wanting to run the model:
# filename_immDyn_seasonalSumm <- "immDyn_seasonalSumm.csv"
# write.csv(ocOut.seasonalSumm, file = paste0("output/Applied/", filename_immDyn_seasonalSumm))
```

# Summary Stats


```{r ocOut.seasonalSumm}

# A.summdf <- A.seasonalSumm %>%
#   mutate(minV = "17w") %>%
#   bind_rows(A2.seasonalSumm %>% mutate(minV = "13w")) %>%
#   mutate(prof_group = ifelse(grepl("*shp*", prof), "shp", "goat"),
#          prof = gsub("oc.","",prof),
#     prof = factor(
#       prof,
#       levels = c("goat.aridP","shp.aridP","goat.semiaridP","shp.semiaridP")))

A.summdf <- A2.seasonalSumm %>% 
  mutate(minV = "13w") %>%
  mutate(prof_group = ifelse(grepl("*shp*", prof), "shp", "goat"),
         prof = gsub("oc.","",prof),
    prof = factor(
      prof,
      levels = c("goat.aridP","shp.aridP","goat.semiaridP","shp.semiaridP")))

validImm <- A.summdf %>%
  select(tenyr_growth, starts_with("imm"), pV, prof, prof_group, minV) %>%
  gather(key = "stat", value = "value", -c(prof, prof_group, pV, minV)) %>%
  mutate(stat = factor(stat, levels = c("imm_V0", "imm_6m", "imm_12m", "imm70_w", "imm70_wAll", "tenyr_growth" )))

####################
## PVIR70 Table ##
###################

validImm_summary <- validImm %>% group_by(stat, pV, prof, minV) %>%
  summarise(mean = mean(value) %>% round(.,digits = 2),
            median = median(value) %>% round(.,digits = 2), 
            min = min(value) %>% round(.,digits = 2), 
            max = max(value) %>% round(.,digits = 2)
            ) %>%
  mutate(median_range = paste0(median," (",min,"-",max,")"))

pvir70_summary <- validImm_summary %>%
  mutate(mean = round(mean, digits = 0), 
         median = round(median, digits = 0), 
         min = round(min, digits = 0),
         max = round(max, digits = 0)) %>%
  filter(stat %in% c("imm70_w", "imm70_wAll")) %>%
  select(-c(median,min,max)) 
pvir70_summary

allprofs <- validImm %>% group_by(stat, pV, minV) %>%
  summarise(mean = mean(value) %>% round(.,digits = 2),
            median = median(value) %>% round(.,digits = 2), 
            min = min(value) %>% round(.,digits = 2), 
            max = max(value) %>% round(.,digits = 2)
            ) %>%
  mutate(median_range = paste0(median," (",min,"-",max,")"))  %>% 
  mutate(mean = round(mean, digits = 0), 
         median = round(median, digits = 0), 
         min = round(min, digits = 0),
         max = round(max, digits = 0)) %>%
  filter(stat %in% c("imm70_w", "imm70_wAll")) %>%
  select(-c(median,min,max)) 
allprofs

if(plotsave){
  write_csv(pvir70_summary, file = "tables/applied/seasonal_pvir70_app.csv")
  write_csv(allprofs, file = "tables/applied/seasonal_pvir70_allprofs_app.csv")
}

```