---
title: "Dynamics testing"
author: "Beth Savagar"
date: "2023-03-14"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# -----------------------
## SETUP ##
# Load libraries, functions etc
library(tidyverse)
library(readr)
library(here)
library(ggpubr)
here()
source("functions/demos_summary.R")
source("functions/output.R")
source("functions/dynmod.R")


```

## Dynamics Model Testing

### Maternal Immunity

- Run model with conditions to replicate Bodjo et al paper where offspring immunity dynamics are drawn from.
- Tested duration of maternal immunity in 112 lambs up to 150 days after birth, born to ewes vaccinated with the homologous PPR vaccine “Nigeria 75/1" at day 90 and day 120 of pregnancy.
- Parameters: 
  - set 112 lambs to immune compartment 
  - set rest of population to 0
  - set mortality, offtake, and all demographic rates (except immune decay) to 0
  - plot proportion immune for first 6 months of simulation
  - plot should mirror the immune decay from Bodjo raw data


```{r maternal-immunity-decay, include = FALSE}
# -----------------------
## PARAMETERS ##

TimeStop_dynamics <- 0.5*52 # 6 months enough for immunity test
TimeStop_transmission <- 24 # 1 day, hourly timestep for transission component
output <- "summary" # define output type "summary" or "count"

# flock_profile <- "imm_test" # "baobab"
# pars_filepath <- paste0("scripts/parameters/set-pars-",flock_profile,".R")
# pars_filepath <- paste0("set-pars-",flock_profile,".R")

# source(pars_filepath)
# source(here("scripts/parameters/set-pars-imm-test.R"))
source(here("scripts","parameters","set-pars-imm-test.R"))

## Transmission Parameters ##
transmission <- F # include transmission? T = Yes, F = No

# transmission_pars <- "fixed"
# transmission_filepath <- paste0("scripts/parameters/set-pars-transmission-",transmission_pars,".R")
# source(transmission_filepath)
source(here("scripts","parameters","set-pars-transmission-fixed.R"))

## Clean Parameters Environment? ##
clean_environment <- T
if(clean_environment == T){
  rm(test_data,test_age_data, kid_f_prop,you_f_prop,juv_f_prop,sub_f_prop,adu_f_prop,
     kid_m_prop,you_m_prop,juv_m_prop,sub_m_prop,adu_m_prop,kid_max, you_max,juv_max,sub_max,max_age_F,max_age_M,
     fIm_init, fS_init, fE_init, fI_init, fR_init,mIm_init, mS_init, mE_init, mI_init, mR_init, off_1,off_F, off_M,mort_1,mort_2,mort_end,birth_r,ppr_mort_1, ppr_mort_2)
}

# -----------------------
## SUMMARY STATS ## 

# create summary data frame to store summary stats for each timestep
summary_df <- output_func(TimeStop_dynamics,output)

# nb need to add if statement to summary (if output == summary, if output == counts)
summary_df <- summary_demos(w=1, f_list, m_list, output, summary_df)


# -----------------------
## MODEL

output_df <- dynmod_func(
  f_list, # initial state of female population
  m_list, # initial state of male population
  TimeStop_dynamics, # 1 year, weekly timestep for demographic component
  TimeStop_transmission, # 1 day, hourly timestep for transission component
  output, # model output: tracker or summary stats
  demographic_pars,
  summary_df
)
```

```{r plotting-1, echo = FALSE, warning = FALSE}
## plotting and analysis

summary_df <- output_df %>%
  mutate(w = as.numeric(w))

p1 <- ggplot(summary_df,aes(x=w,y=sum_pop))+
  geom_line(size = 1.5)+
  labs(title = "Total Population",
       x="time (weeks)", 
       y = "total population")+
  theme_bw()


## melt summary_df to long format
summary_long <- summary_df %>%
  gather(key="stat", value="prop", -w)


## create df for different stats:

colors_agesex <- RColorBrewer::brewer.pal(6,"Set1")
colors_agesex[6] <- "black"
  
# age-sex
summary_agesex <- summary_long %>%
  filter(!stat %in% c("sum_pop",
                      "prop_inf",
                      "prop_immune")) %>%
  mutate(stat = ordered(stat, 
                        levels = c("pKid", "pYou", "pJuv", "pSub", "pAdu", "pF")))


## Plots:
# age-sex proportions
p2 <- ggplot(summary_agesex, aes(x=w, y=prop, group=stat, col=stat))+
  geom_line(size=1)+
  # scale_color_brewer(palette = "Set1")+
  scale_color_manual(values = colors_agesex)+
  labs(x = "weeks", y = "Proportion of total population", col = "age-sex cat")+
  theme_bw()

# immunity
p3 <- ggplot(summary_df, aes(x=w, y=prop_immune))+
  geom_line()+
  geom_line(data = imm_decay_corrected, aes(x=wk, y=imm), col = "red")+coord_cartesian(xlim=c(0,20))+
  scale_x_continuous(breaks = seq(0,20,1))+
  scale_y_continuous(breaks = seq(0,1,0.1))
  # geom_point(data = data.frame("w"=1:length(immunity),"imm"=immunity), aes(x=w, y=imm), col ="blue")+

p1
p2
p3
```

