---
title: "Dynamics Model Testing"
author: "Beth Savagar"
date: "2023-03-14"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# -----------------------
## SETUP ##
# Load libraries, functions etc
library(tidyverse)
library(readr)
library(here)
library(ggpubr)
library(knitr)
here()
source("functions/demos_summary.R")
source("functions/output.R")
source("functions/dynmod.R")


```

## Maternal Immunity

- Check implementation of maternal immunity decay by comparing model output to empirical data (from Bodjo *et al*)
- Run model with conditions to replicate Bodjo *et al*
- Bodjo *et al* tested the duration of maternal immunity in 112 lambs up to 150 days after birth, born to ewes vaccinated with the homologous PPR vaccine “Nigeria 75/1" at day 90 and day 120 of pregnancy.
- Parameters: 
  - set 112 lambs to immune offspring compartment 
  - set rest of population to 0
  - set mortality, offtake, and all demographic rates (except maternal immune decay) to 0
  - set M:F ratio to 1:1
  - plot proportion immune for first 6 months of simulation
  - plot should mirror the immune decay from Bodjo raw data.  
  <br>

```{r maternal-immunity-decay, include = FALSE}
# -----------------------
## PARAMETERS ##

TimeStop_dynamics <- 0.5*52 # 6 months enough for immunity test
TimeStop_transmission <- 24 # 1 day, hourly timestep for transission component
output <- "summary" # define output type "summary" or "count"

# flock_profile <- "imm_test" # "baobab"
# pars_filepath <- paste0("scripts/parameters/set-pars-",flock_profile,".R")
# pars_filepath <- paste0("set-pars-",flock_profile,".R")

# source(pars_filepath)
# source(here("scripts/parameters/set-pars-imm-test.R"))
source(here("scripts","parameters","set-pars-imm-test.R"))

## Transmission Parameters ##
transmission <- F # include transmission? T = Yes, F = No

# transmission_pars <- "fixed"
# transmission_filepath <- paste0("scripts/parameters/set-pars-transmission-",transmission_pars,".R")
# source(transmission_filepath)
source(here("scripts","parameters","set-pars-transmission-fixed.R"))

## Clean Parameters Environment? ##
clean_environment <- T
if(clean_environment == T){
  rm(test_data,test_age_data, kid_f_prop,you_f_prop,juv_f_prop,sub_f_prop,adu_f_prop,
     kid_m_prop,you_m_prop,juv_m_prop,sub_m_prop,adu_m_prop,kid_max, you_max,juv_max,sub_max,max_age_F,max_age_M,
     fIm_init, fS_init, fE_init, fI_init, fR_init,mIm_init, mS_init, mE_init, mI_init, mR_init, off_1,off_F, off_M,mort_1,mort_2,mort_end,birth_r,ppr_mort_1, ppr_mort_2)
}

# -----------------------
## SUMMARY STATS ## 

# create summary data frame to store summary stats for each timestep
summary_df <- output_func(TimeStop_dynamics,output)

# nb need to add if statement to summary (if output == summary, if output == counts)
summary_df <- summary_demos(w=1, f_list, m_list, output, summary_df)


# -----------------------
## MODEL

output_df <- dynmod_func(
  f_list, # initial state of female population
  m_list, # initial state of male population
  TimeStop_dynamics, # 1 year, weekly timestep for demographic component
  TimeStop_transmission, # 1 day, hourly timestep for transission component
  output, # model output: tracker or summary stats
  demographic_pars,
  summary_df
)
```

```{r mat_imm_plots, echo = FALSE, warning = FALSE}
## plotting and analysis

summary_df <- output_df %>%
  mutate(w = as.numeric(w))

p1 <- ggplot(summary_df,aes(x=w,y=sum_pop))+
  geom_line(size = 1.5)+
  labs(title = "Total Population",
       x="time (weeks)", 
       y = "total population")+
  theme_bw()


## melt summary_df to long format
summary_long <- summary_df %>%
  gather(key="stat", value="prop", -w)


## create df for different stats:

colors_agesex <- RColorBrewer::brewer.pal(6,"Set1")
colors_agesex[6] <- "black"
  
# age-sex
summary_agesex <- summary_long %>%
  filter(!stat %in% c("sum_pop",
                      "prop_inf",
                      "prop_immune")) %>%
  mutate(stat = ordered(stat, 
                        levels = c("pKid", "pYou", "pJuv", "pSub", "pAdu", "pF")))


## Plots:
# age-sex proportions
p2 <- ggplot(summary_agesex, aes(x=w, y=prop, group=stat, col=stat))+
  geom_line(size=1)+
  # scale_color_brewer(palette = "Set1")+
  scale_color_manual(values = colors_agesex)+
  # facet_wrap(~stat,ncol=1)+
  labs(title = "Population Proportion",
       x = "weeks", 
       y = "Proportion of total population", 
       col = "age-sex cat")+
  theme_bw()

# immunity

imm_data <- summary_df %>%
  select(w, imm = prop_immune) %>% 
  mutate(source = "model") %>%
  rbind(imm_decay_corrected %>% select("w"=wk, imm) %>% mutate(source = "bodjo"))

p3 <- ggplot(imm_data, aes(x=w, y=imm))+
  geom_line(aes(col = source))+
  # geom_line(data = imm_decay_corrected, aes(x=wk, y=imm), col = "red")+
  coord_cartesian(xlim=c(0,20))+
  scale_x_continuous(breaks = seq(0,20,1))+
  scale_y_continuous(breaks = seq(0,1,0.1))+
  scale_color_manual(values = c("model" = "black", "bodjo" = "red"))+
  labs(title = "Immune Dynamics",
       x = "Weeks",
       y = " Proportion Immune")+
  theme_bw()

  # geom_point(data = data.frame("w"=1:length(immunity),"imm"=immunity), aes(x=w, y=imm), col ="blue")+
```


```{r immplot1, echo = FALSE, warning = FALSE, fig.height = 2.5}
ggarrange(p1,p2,nrow=1)
```

*Maternal Immunity Interpretation*

- The population remains constants at 112 animals for the duration of the simulation
- All animals begin in the `pKid` compartment, and move into the `pYou` compartment at week 18

```{r immplot2, echo = FALSE, warning = FALSE, fig.width = 6, fig.height = 3}
p3
```

*Maternal Immunity Interpretation*

- The model exactly replicates immune decay from Bodjo data
- The apparent 1 week lapse is because the model starts at week 1 with 100% offspring in the immune compartment
<br>

## Demographic Processes: Basic Model

1) Do animals move through age compartments as expected?
- Parameters:
  - Set the population to 100 animals
  - Assign all animals to S1 age group (first age-group, susceptible offspring)
  - Set all demographic parameters (births, deaths, intake, offtake, maternal immunity) to 0
  - Set the max life-span of males and females to 5years
  - Set M:F ratio as 1:1
  - Animals should move through age compartments uniformly, at 5 years population will die out.

*NB: NaN values due to dividing by 0 when population dies out (fix this in `demos_summary.R`)*
<br>

```{r basic-model, include = FALSE}
# -----------------------
## PARAMETERS ##

TimeStop_dynamics <- 6*52 # 6 years to review 5 year age span
TimeStop_transmission <- 24 # 1 day, hourly timestep for transission component
output <- "summary" # define output type "summary" or "count"

# test_1 dataset, all aprameters set to 0 and all animals in age group 1 (susceptible)
dataset1 <- "test_1" # select dataset for test data
dataset2 <- "test_1" # select dataset for age data

source(here("scripts","parameters","set-pars-test.R"))

## Transmission Parameters ##
transmission <- F # include transmission? T = Yes, F = No

# transmission_pars <- "fixed"
# transmission_filepath <- paste0("scripts/parameters/set-pars-transmission-",transmission_pars,".R")
# source(transmission_filepath)
source(here("scripts","parameters","set-pars-transmission-fixed.R"))

## Clean Parameters Environment? ##
clean_environment <- T
if(clean_environment == T){
  rm(test_data,test_age_data, kid_f_prop,you_f_prop,juv_f_prop,sub_f_prop,adu_f_prop,
     kid_m_prop,you_m_prop,juv_m_prop,sub_m_prop,adu_m_prop,kid_max, you_max,juv_max,sub_max,max_age_F,max_age_M,
     fIm_init, fS_init, fE_init, fI_init, fR_init,mIm_init, mS_init, mE_init, mI_init, mR_init, off_1,off_F, off_M,mort_1,mort_2,mort_end,birth_r,ppr_mort_1, ppr_mort_2)
}

# -----------------------
## SUMMARY STATS ## 

# create summary data frame to store summary stats for each timestep
summary_df <- output_func(TimeStop_dynamics,output)

# nb need to add if statement to summary (if output == summary, if output == counts)
summary_df <- summary_demos(w=1, f_list, m_list, output, summary_df)


# -----------------------
## MODEL

output_df <- dynmod_func(
  f_list, # initial state of female population
  m_list, # initial state of male population
  TimeStop_dynamics, # 1 year, weekly timestep for demographic component
  TimeStop_transmission, # 1 day, hourly timestep for transission component
  output, # model output: tracker or summary stats
  demographic_pars,
  summary_df
)
```

```{r plotting-2, echo = FALSE, warning = FALSE}
## plotting and analysis

summary_df <- output_df %>%
  mutate(w = as.numeric(w))

p1 <- ggplot(summary_df,aes(x=w,y=sum_pop))+
  geom_line(size = 1.5)+
  labs(title = "Total Population",
       x="time (weeks)", 
       y = "total population")+
  theme_bw()


## melt summary_df to long format
summary_long <- summary_df %>%
  gather(key="stat", value="prop", -w)


## create df for different stats:

colors_agesex <- RColorBrewer::brewer.pal(6,"Set1")
colors_agesex[6] <- "black"
  
# age-sex
summary_agesex <- summary_long %>%
  filter(!stat %in% c("sum_pop",
                      "prop_inf",
                      "prop_immune")) %>%
  mutate(stat = ordered(stat, 
                        levels = c("pKid", "pYou", "pJuv", "pSub", "pAdu", "pF")))


## Plots:
# age-sex proportions
p2 <- ggplot(summary_agesex, aes(x=w, y=prop, group=stat, col=stat))+
  geom_line(size=1)+
  # scale_color_brewer(palette = "Set1")+
  scale_color_manual(values = colors_agesex)+
  labs(title = "Population Proportion",
       x = "weeks", 
       y = "Proportion of total population", 
       col = "age-sex cat")+
  facet_wrap(~stat)+
  theme_bw()

# immunity
p3 <- ggplot(summary_df, aes(x=w, y=prop_immune))+
  geom_line()+
  coord_cartesian(xlim=c(0,20))+
  scale_x_continuous(breaks = seq(0,20,1))+
  scale_y_continuous(breaks = seq(0,1,0.1))+
  labs(title = "Immune Dynamics",
       x = "Weeks",
       y = " Proportion Immune")+
  theme_bw()
  # geom_point(data = data.frame("w"=1:length(immunity),"imm"=immunity), aes(x=w, y=imm), col ="blue")+
```

```{r test1plot1, echo = FALSE, warning = FALSE, fig.height = 2.5, fig.width = 3}
p1
# p3 - don't need immune dynamics to be plotted
```

```{r test1plot2, echo = FALSE, warning = FALSE}
p2

```

*Basic Model Interpretation* 

- The population remains constant up to 5 years (week 260)
- Animals move through discrete age groups uniformly as expected
<br>
  

## Mortality 
2) Check that model with mortality functions as expected i.e. should be able to analytically solve population decline?
- Parameters:
  - Set the population to 100 animals
  - Assign all animals to S1 age group (first age-group, susceptible offspring)
  - Set **mortality rate** to 0.01 per week
  - Set all other demographic parameters (births, intake, offtake, maternal immunity) to 0
  - Set the max life-span of males and females to 5years
  - Set M:F ratio as 1:1
  - Animals should move through age groups, with constant mortality rate, until 5 years
  
**Test validation: what is the gradient of the curve?**

- *Limited time to run tests so this is basic validation...*
- Briefly: 
  - The mortality rate is 0.01/week in all age groups
  - Therefore survival is 0.99/week
  - Given survival we can calculate the expected population size after e.g. 1year, 5 years, and compare this to model output.
  - Expected 1 year survival = $0.99^{52} = 0.59$ 
  - Expected 5 year survival = $0.99^{(52*5)} = 0.07$
  - Compare these figures to model output (`output_df`) below...
  - *Calculate gradient of the curve..?*

```{r mortality, include = FALSE}
# -----------------------
## PARAMETERS ##

TimeStop_dynamics <- 6*52 # 6 years to review 5 year age span
TimeStop_transmission <- 24 # 1 day, hourly timestep for transission component
output <- "summary" # define output type "summary" or "count"

# test_1 dataset, all aprameters set to 0 and all animals in age group 1 (susceptible)
dataset1 <- "test_mortality" # select dataset for test data
dataset2 <- "test_1" # test_1 age data sets all animals to first age group

source(here("scripts","parameters","set-pars-test.R"))

## Transmission Parameters ##
transmission <- F # include transmission? T = Yes, F = No

# transmission_pars <- "fixed"
# transmission_filepath <- paste0("scripts/parameters/set-pars-transmission-",transmission_pars,".R")
# source(transmission_filepath)
source(here("scripts","parameters","set-pars-transmission-fixed.R"))

## Clean Parameters Environment? ##
clean_environment <- T
if(clean_environment == T){
  rm(test_data,test_age_data, kid_f_prop,you_f_prop,juv_f_prop,sub_f_prop,adu_f_prop,
     kid_m_prop,you_m_prop,juv_m_prop,sub_m_prop,adu_m_prop,kid_max, you_max,juv_max,sub_max,max_age_F,max_age_M,
     fIm_init, fS_init, fE_init, fI_init, fR_init,mIm_init, mS_init, mE_init, mI_init, mR_init, off_1,off_F, off_M,mort_1,mort_2,mort_end,birth_r,ppr_mort_1, ppr_mort_2)
}

# -----------------------
## SUMMARY STATS ## 

# create summary data frame to store summary stats for each timestep
summary_df <- output_func(TimeStop_dynamics,output)

# nb need to add if statement to summary (if output == summary, if output == counts)
summary_df <- summary_demos(w=1, f_list, m_list, output, summary_df)


# -----------------------
## MODEL

output_df <- dynmod_func(
  f_list, # initial state of female population
  m_list, # initial state of male population
  TimeStop_dynamics, # 1 year, weekly timestep for demographic component
  TimeStop_transmission, # 1 day, hourly timestep for transission component
  output, # model output: tracker or summary stats
  demographic_pars,
  summary_df
)
```

```{r plotting-3, echo = FALSE, warning = FALSE}
## plotting and analysis

summary_df <- output_df %>%
  mutate(w = as.numeric(w))

p1 <- ggplot(summary_df,aes(x=w,y=sum_pop))+
  geom_line(size = 1.5)+
  labs(title = "Total Population",
       x="time (weeks)", 
       y = "total population")+
  theme_bw()


## melt summary_df to long format
summary_long <- summary_df %>%
  gather(key="stat", value="prop", -w)


## create df for different stats:

colors_agesex <- RColorBrewer::brewer.pal(6,"Set1")
colors_agesex[6] <- "black"
  
# age-sex
summary_agesex <- summary_long %>%
  filter(!stat %in% c("sum_pop",
                      "prop_inf",
                      "prop_immune")) %>%
  mutate(stat = ordered(stat, 
                        levels = c("pKid", "pYou", "pJuv", "pSub", "pAdu", "pF")))


## Plots:
# age-sex proportions
p2 <- ggplot(summary_agesex, aes(x=w, y=prop, group=stat, col=stat))+
  geom_line(size=1)+
  # scale_color_brewer(palette = "Set1")+
  scale_color_manual(values = colors_agesex)+
  labs(title = "Population Proportion",
       x = "weeks", 
       y = "Proportion of total population", 
       col = "age-sex cat")+
  theme_bw()

# immunity
p3 <- ggplot(summary_df, aes(x=w, y=prop_immune))+
  geom_line()+
  coord_cartesian(xlim=c(0,20))+
  scale_x_continuous(breaks = seq(0,20,1))+
  scale_y_continuous(breaks = seq(0,1,0.1))+
  labs(title = "Immune Dynamics",
       x = "Weeks",
       y = " Proportion Immune")+
  theme_bw()
  # geom_point(data = data.frame("w"=1:length(immunity),"imm"=immunity), aes(x=w, y=imm), col ="blue")+


surv <- output_df %>% 
  filter(w %in% c(53,260)) %>% 
  select("weeks" = w, "Population" = sum_pop) %>% 
  mutate(Population = round(Population, 2)) %>%
  knitr::kable()
```
<br>

- Model population output: 
```{r mort_output, echo = F, fig.width = 3, fig.height = 3}

surv

p1
# p2 - don't need to plot sex-age structure
# p3 - don't need immune dynamics to be plotted
```

*Mortality Interpretation*

- Model output for population size at years 1 (N = 59.3) and year 5 (N = 7.4) equal to expected population size based on mortality of 0.01 (survival of 0.99)

\newpage

## Further Tests - to be completed

## Births 

3) Check model function with birth rate - slightly tricky as rate is per adult F
- Parameters:
  - Set the population to 100 animals
  - Assign all animals to S59 - first adult age category, 50:50 M:F
  - Set **birth rate** to 0.02 per week (2*0.01, pop birth rate of 0.01, f birth rate of 0.02)
  - Set all other demographic parameters (deaths, intake, offtake, maternal immunity) to 0
  - Set the max life-span of males and females to 10 years
  - Set M:F ratio as 1:1
  - Expect exponential growth, initially with rate of 0.01 (for population), this will change as young reach maturity
  
**Test validation: what is the gradient of the curve?**
  
  
```{r birth, include = FALSE}
# -----------------------
## PARAMETERS ##

TimeStop_dynamics <- 6*52 # 6 years to review 5 year age span
TimeStop_transmission <- 24 # 1 day, hourly timestep for transission component
output <- "summary" # define output type "summary" or "count"

# test_birth dataset, all aprameters set to 0 and all animals in first adult age group 1 (susceptible)
dataset1 <- "test_birth" # select dataset for test data
dataset2 <- "test_birth" # test_birth age data sets all animals to first adult age group

source(here("scripts","parameters","set-pars-test.R"))

## Transmission Parameters ##
transmission <- F # include transmission? T = Yes, F = No

# transmission_pars <- "fixed"
# transmission_filepath <- paste0("scripts/parameters/set-pars-transmission-",transmission_pars,".R")
# source(transmission_filepath)
source(here("scripts","parameters","set-pars-transmission-fixed.R"))

## Clean Parameters Environment? ##
clean_environment <- T
if(clean_environment == T){
  rm(test_data,test_age_data, kid_f_prop,you_f_prop,juv_f_prop,sub_f_prop,adu_f_prop,
     kid_m_prop,you_m_prop,juv_m_prop,sub_m_prop,adu_m_prop,kid_max, you_max,juv_max,sub_max,max_age_F,max_age_M,
     fIm_init, fS_init, fE_init, fI_init, fR_init,mIm_init, mS_init, mE_init, mI_init, mR_init, off_1,off_F, off_M,mort_1,mort_2,mort_end,birth_r,ppr_mort_1, ppr_mort_2)
}

# -----------------------
## SUMMARY STATS ## 

# create summary data frame to store summary stats for each timestep
summary_df <- output_func(TimeStop_dynamics,output)

# nb need to add if statement to summary (if output == summary, if output == counts)
summary_df <- summary_demos(w=1, f_list, m_list, output, summary_df)


# -----------------------
## MODEL

output_df <- dynmod_func(
  f_list, # initial state of female population
  m_list, # initial state of male population
  TimeStop_dynamics, # 1 year, weekly timestep for demographic component
  TimeStop_transmission, # 1 day, hourly timestep for transission component
  output, # model output: tracker or summary stats
  demographic_pars,
  summary_df
)
```

```{r plotting-birth, echo = FALSE, warning = FALSE}
## plotting and analysis

summary_df <- output_df %>%
  mutate(w = as.numeric(w))

p1 <- ggplot(summary_df,aes(x=w,y=sum_pop))+
  geom_line(size = 1.5)+
  labs(title = "Total Population",
       x="time (weeks)", 
       y = "total population")+
  theme_bw()


## melt summary_df to long format
summary_long <- summary_df %>%
  gather(key="stat", value="prop", -w)


## create df for different stats:

colors_agesex <- RColorBrewer::brewer.pal(6,"Set1")
colors_agesex[6] <- "black"
  
# age-sex
summary_agesex <- summary_long %>%
  filter(!stat %in% c("sum_pop",
                      "prop_inf",
                      "prop_immune")) %>%
  mutate(stat = ordered(stat, 
                        levels = c("pKid", "pYou", "pJuv", "pSub", "pAdu", "pF")))


## Plots:
# age-sex proportions
p2 <- ggplot(summary_agesex, aes(x=w, y=prop, group=stat, col=stat))+
  geom_line(size=1)+
  # scale_color_brewer(palette = "Set1")+
  scale_color_manual(values = colors_agesex)+
  labs(title = "Population Proportion",
       x = "weeks", 
       y = "Proportion of total population", 
       col = "age-sex cat")+
  theme_bw()

# immunity
p3 <- ggplot(summary_df, aes(x=w, y=prop_immune))+
  geom_line()+
  coord_cartesian(xlim=c(0,20))+
  scale_x_continuous(breaks = seq(0,20,1))+
  scale_y_continuous(breaks = seq(0,1,0.1))+
  labs(title = "Immune Dynamics",
       x = "Weeks",
       y = " Proportion Immune")+
  theme_bw()
  # geom_point(data = data.frame("w"=1:length(immunity),"imm"=immunity), aes(x=w, y=imm), col ="blue")+
```
<br>

```{r birth_output, echo = F, fig.width = 3, fig.height = 3}

p1
p2
# p3 - don't need immune dynamics to be plotted
```

*Birth Interpretation*

- How do I calculate overall birth rate, especially given that my input parameter is the adult female birth rate
- For timesteps 1-78 there should be a constant population growth: 
  - the adult female population remains constant at 50 individuals (as all start in 1st adult age cat + no mortality)
  - the birth rate remains constant at 0.02
  - At each timestep $rN_f$ new offspring are born ($r$ is birth rate per adult female - 0.02 - and $N_f$ is the female population - 50 -)
  - For timesteps 1-71 (i.e. 70 timesteps): $B = t(rN_f) = 70*(0.02*50)$, hence $B=70$
  - Expect 70 new births, with initial population of 100, population at timestep 71 should be 170, as below
- beyond timestep 78 this becomes more confusing since new animals start to join the Adu_F age cat + reproduce
  
```{r birth_validation, echo = F, fig.width = 3, fig.height = 3}
  
summary_df %>% filter(w %in% c(1,71)) %>% select(w,sum_pop) %>% kable()

```



## Births-Deaths Test: Stable Population

4) Attempt to find conditions under which population is stable (this is the closest I managed)
- Parameters:
  - Set the population to 100 animals
  - Proportion of animals in each age cat - defined based on stable state output of this simulation:
    - Kid: 0.1592371, You:0.07376386, Juv: 0.1787116, Sub: 0.1370716, Adu: 0.4512159
  - **Mortality Rate** set at 0.01 for all animals (Young + Adult)
  - Attempted to match this defining **Birth Rate** for adult females at 0.02 initially
    - through trial and error **Birth Rate** of 0.045 gave the below result...
  - All other demographic parameters (intake, offtake, maternal immunity) set to 0
  - Set the max life-span of males and females to 50 years
    - Obviously unrealistic but meant I avoided contending with slaughter of all animals at max_age and could observe population trend over longer simulation time.
  - Set M:F ratio as 1:1
  - See test_parameters.csv : births_deaths for details
  - *Attempt to find a solution where the population is stable*


```{r birth_death, include = FALSE}
# -----------------------
## PARAMETERS ##

TimeStop_dynamics <- 25*52 # 6 years to review 5 year age span
TimeStop_transmission <- 24 # 1 day, hourly timestep for transission component
output <- "summary" # define output type "summary" or "count"

# test_birth dataset, all aprameters set to 0 and all animals in first adult age group 1 (susceptible)
dataset1 <- "test_birth_death" # select dataset for test data
dataset2 <- "test_birth_death" # test_birth age data sets all animals to first adult age group

source(here("scripts","parameters","set-pars-test.R"))

## Transmission Parameters ##
transmission <- F # include transmission? T = Yes, F = No

# transmission_pars <- "fixed"
# transmission_filepath <- paste0("scripts/parameters/set-pars-transmission-",transmission_pars,".R")
# source(transmission_filepath)
source(here("scripts","parameters","set-pars-transmission-fixed.R"))

## Clean Parameters Environment? ##
clean_environment <- T
if(clean_environment == T){
  rm(test_data,test_age_data, kid_f_prop,you_f_prop,juv_f_prop,sub_f_prop,adu_f_prop,
     kid_m_prop,you_m_prop,juv_m_prop,sub_m_prop,adu_m_prop,kid_max, you_max,juv_max,sub_max,max_age_F,max_age_M,
     fIm_init, fS_init, fE_init, fI_init, fR_init,mIm_init, mS_init, mE_init, mI_init, mR_init, off_1,off_F, off_M,mort_1,mort_2,mort_end,birth_r,ppr_mort_1, ppr_mort_2)
}

# -----------------------
## SUMMARY STATS ## 

# create summary data frame to store summary stats for each timestep
summary_df <- output_func(TimeStop_dynamics,output)

# nb need to add if statement to summary (if output == summary, if output == counts)
summary_df <- summary_demos(w=1, f_list, m_list, output, summary_df)


# -----------------------
## MODEL

output_df <- dynmod_func(
  f_list, # initial state of female population
  m_list, # initial state of male population
  TimeStop_dynamics, # 1 year, weekly timestep for demographic component
  TimeStop_transmission, # 1 day, hourly timestep for transission component
  output, # model output: tracker or summary stats
  demographic_pars,
  summary_df
)
```

```{r plotting-birth_death, echo = FALSE, warning = FALSE}
## plotting and analysis

summary_df <- output_df %>%
  mutate(w = as.numeric(w))

p1 <- ggplot(summary_df,aes(x=w,y=sum_pop))+
  geom_line(size = 1.5)+
  labs(title = "Total Population",
       x="time (weeks)", 
       y = "total population")+
  coord_cartesian(ylim=c(0,NA))+
  theme_bw()


## melt summary_df to long format
summary_long <- summary_df %>%
  gather(key="stat", value="prop", -w)


## create df for different stats:

colors_agesex <- RColorBrewer::brewer.pal(6,"Set1")
colors_agesex[6] <- "black"
  
# age-sex
summary_agesex <- summary_long %>%
  filter(!stat %in% c("sum_pop",
                      "prop_inf",
                      "prop_immune")) %>%
  mutate(stat = ordered(stat, 
                        levels = c("pKid", "pYou", "pJuv", "pSub", "pAdu", "pF")))


## Plots:
# age-sex proportions
p2 <- ggplot(summary_agesex, aes(x=w, y=prop, group=stat, col=stat))+
  geom_line(size=1)+
  # scale_color_brewer(palette = "Set1")+
  scale_color_manual(values = colors_agesex)+
  labs(title = "Population Proportion",
       x = "weeks", 
       y = "Proportion of total population", 
       col = "age-sex cat")+
  theme_bw()

# immunity
p3 <- ggplot(summary_df, aes(x=w, y=prop_immune))+
  geom_line()+
  coord_cartesian(xlim=c(0,20))+
  scale_x_continuous(breaks = seq(0,20,1))+
  scale_y_continuous(breaks = seq(0,1,0.1))+
  labs(title = "Immune Dynamics",
       x = "Weeks",
       y = " Proportion Immune")+
  theme_bw()
  # geom_point(data = data.frame("w"=1:length(immunity),"imm"=immunity), aes(x=w, y=imm), col ="blue")+
```
<br>

```{r birthdeath_output, echo = F, fig.width = 3, fig.height = 3}

p1
p2
# p3 - don't need immune dynamics to be plotted
```

*Births - Deaths Interpretation*

Crude validation:  

- Given death rate of 0.01 for all age groups
- Mature female birth rate of 0.045
- To get a fixed population size of which the above is an approximation we need an overall birth rate of 0.01
- Here we have a pop of 100...
- The proportion in each age group is stable at: 
  - Kid: 0.1592371 You:0.07376386 Juv: 0.1787116 Sub: 0.1370716 Adu: 0.4512159
- Hence the adult female proportion is: adu_f ~ 0.225
- To calculate overall birth rate from female birth rate: 
  - $ B_{total} =  ( B_f * p_{aduF}  *N) /N = B_f * p_{aduF} $
- So: 
  - $ B_{total} = 0.045 * 0.225 = 0.010125 $ approx equal to the birth rate of 0.01
  
- *Reversing this: given population birth rate and stable age-sex structure ($p_{aduF}$):*
  - $ B_{total} / p_{aduF}  = B_f $. 
  
- **Whilst this is not a tidy proof it satisfies me that a constant population size can be approximated if the birth and death rates are equal**
 
  
  

### Population Size


### Population Structure


\newpage

## BAOBAB data

- Test model using demographic rates from (simple) BAOBAB dataset
- Parameters calculated from data supplied by Andrea from Louga & Kolda (Senegal) Sheep & Goats
- Here use Kolga Goats data
  - Data provided as monthly rates
  - For testing calculate median monthly rates 
  - Convert to weekly rate by dividing median monthly rate by 4.345 (av. wk/mnth)
  - See `'~/OneDrive - Royal Veterinary College/PPR Collaborations/Data Bank/Baobab_data (Apr2021)/look-at-data.R'` for details

- Parameters:
  - mortality: 0.00537 (constant for all youth, adult, m, f)
  - births: 0.023 (adult F only)
  - intake: 0.0121
  - offtake: 0.0121
  - NET offtake: 0
  - Population: 100
  - M:F ratio (0.25:0.75)
  - Population proportions: 
    - `Kid` (0.05), 
    - `You` (0.05), 
    - `Juv` (0.2), 
    - `Sub_M` (0.05), `Sub_F` (0.15), 
    - `Adu_M` (0.05), `Adu_F` (0.45)
    
- *NB: data for population size, M:F ratio and population proportions are estimates, not provided in Baobab dataset*
<br>

```{r baobab, include = FALSE}
# see source("~/OneDrive - Royal Veterinary College/PPR Collaborations/Data Bank/Baobab_data (Apr2021)/look-at-data.R")
# -----------------------
## PARAMETERS ##

TimeStop_dynamics <- 10*52 # 6 years to review 5 year age span
TimeStop_transmission <- 24 # 1 day, hourly timestep for transission component
output <- "summary" # define output type "summary" or "count"

# test_1 dataset, all aprameters set to 0 and all animals in age group 1 (susceptible)
dataset1 <- "test_baobab" # select dataset for test data
dataset2 <- "test_baobab" # select dataset for age data

source(here("scripts","parameters","set-pars-test.R"))

## Transmission Parameters ##
transmission <- F # include transmission? T = Yes, F = No

# transmission_pars <- "fixed"
# transmission_filepath <- paste0("scripts/parameters/set-pars-transmission-",transmission_pars,".R")
# source(transmission_filepath)
source(here("scripts","parameters","set-pars-transmission-fixed.R"))

## Clean Parameters Environment? ##
clean_environment <- T
if(clean_environment == T){
  rm(test_data,test_age_data, kid_f_prop,you_f_prop,juv_f_prop,sub_f_prop,adu_f_prop,
     kid_m_prop,you_m_prop,juv_m_prop,sub_m_prop,adu_m_prop,kid_max, you_max,juv_max,sub_max,max_age_F,max_age_M,
     fIm_init, fS_init, fE_init, fI_init, fR_init,mIm_init, mS_init, mE_init, mI_init, mR_init, off_1,off_F, off_M,mort_1,mort_2,mort_end,birth_r,ppr_mort_1, ppr_mort_2)
}

# -----------------------
## SUMMARY STATS ## 

# create summary data frame to store summary stats for each timestep
summary_df <- output_func(TimeStop_dynamics,output)

# nb need to add if statement to summary (if output == summary, if output == counts)
summary_df <- summary_demos(w=1, f_list, m_list, output, summary_df)


# -----------------------
## MODEL

output_df <- dynmod_func(
  f_list, # initial state of female population
  m_list, # initial state of male population
  TimeStop_dynamics, # 1 year, weekly timestep for demographic component
  TimeStop_transmission, # 1 day, hourly timestep for transission component
  output, # model output: tracker or summary stats
  demographic_pars,
  summary_df
)
```

```{r baobabplot, echo = FALSE, warning = FALSE}
## plotting and analysis

summary_df <- output_df %>%
  mutate(w = as.numeric(w))

p1 <- ggplot(summary_df,aes(x=w,y=sum_pop))+
  geom_line(size = 1.5)+
  labs(title = "Total Population",
       x="time (weeks)", 
       y = "total population")+
  theme_bw()


## melt summary_df to long format
summary_long <- summary_df %>%
  gather(key="stat", value="prop", -w)


## create df for different stats:

colors_agesex <- RColorBrewer::brewer.pal(6,"Set1")
colors_agesex[6] <- "black"
  
# age-sex
summary_agesex <- summary_long %>%
  filter(!stat %in% c("sum_pop",
                      "prop_inf",
                      "prop_immune")) %>%
  mutate(stat = ordered(stat, 
                        levels = c("pKid", "pYou", "pJuv", "pSub", "pAdu", "pF")))


## Plots:
# age-sex proportions
p2 <- ggplot(summary_agesex, aes(x=w, y=prop, group=stat, col=stat))+
  geom_line(size=1)+
  # scale_color_brewer(palette = "Set1")+
  scale_color_manual(values = colors_agesex)+
  labs(title = "Population Proportion",
       x = "weeks", 
       y = "Proportion of total population", 
       col = "age-sex cat")+
  theme_bw()

# immunity
p3 <- ggplot(summary_df, aes(x=w, y=prop_immune))+
  geom_line()+
  coord_cartesian(xlim=c(0,20))+
  scale_x_continuous(breaks = seq(0,20,1))+
  scale_y_continuous(breaks = seq(0,1,0.1))+
  labs(title = "Immune Dynamics",
       x = "Weeks",
       y = " Proportion Immune")+
  theme_bw()
  # geom_point(data = data.frame("w"=1:length(immunity),"imm"=immunity), aes(x=w, y=imm), col ="blue")+
```

```{r bbplot1, echo = FALSE, warning = FALSE, fig.height = 2.5}
ggarrange(p1,p2,nrow=1)
```




